---
title: "Reproducible data analysis: thesis data analysis and visualization"
subtitle: "Pacific Maritime forWater Masters Project (NSERC forWater)"
author: "Hannah J McSorley"
date: "2020-01-31"
output:
  word_document:
    toc: true
    reference_docx: word-styles-document_thesis.docx
bibliography: library.bib  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

If needed, install required packages:
```
install.packages("tidyverse")
install.packages("knitr")      
install.packages("gridExtra")  
install.packages("grid") 
install.packages("viridis")
```

```{r packages, include = FALSE}

# load packages
suppressPackageStartupMessages(library(tidyverse))  # includes: dplyr, ggplot2, purrr, readr, forcats, lubridate
suppressPackageStartupMessages(library(knitr))      # tidy tables
suppressPackageStartupMessages(library(gridExtra))  # rapid runoff hydrograph/precip plots
suppressPackageStartupMessages(library(grid))       # for rapid runoff plots
suppressPackageStartupMessages(library(ggplot2))    # plots
suppressPackageStartupMessages(library(viridis))    # nice colours for plots gradient fills

```


# File Inputs

Results of data wrangling (01) were saved as .csv files for tidy loading. Load those files now for analysis and 
Keep this as a code-note so to prevent accidental mis-handling of data.

``` 
# {r output sample analysis files}

## save all compiled sample analysis as .csv files 
# keep as code note to avoid accidental over-writing later*

# TOCV_results df
# Shimadzu sample analyses results
write_csv(TOCV_results, path = "R-outputs_UBC-forWater-MSc_HMc/01_TOCV_results.csv", na = "NA")   

# SCAN_results df
# Spectrolyser sample analyses results
write_csv(SCAN_results, path = "R-outputs_UBC-forWater-MSc_HMc/01_SCAN-par_results.csv", na = "NA")               

# FULLSCAN_results df
# Spectrolyser fullscan (.fp) analyses results
write_csv(FULLSCAN_results, path = "R-outputs_UBC-forWater-MSc_HMc/01_SCAN-fp_results.csv", na = "NA")               

# sampleresults df
# compiled sample analyses results (wide)
write_csv(sampleresults, path = "R-outputs_UBC-forWater-MSc_HMc/01_Lab-analyses_sample-results_wide.csv", na = "NA")  

# odyssey_data df
# stage data compiled with interval/trip
write_csv(odyssey_data, path = "R-outputs_UBC-forWater-MSc_HMc/01_Odyssey-stage_compiled.csv", na = "NA")

# precip_data df
# 2018-2020 weather station data compiled and formatted
write_csv(precip_data, path = "R-outputs_UBC-forWater-MSc_HMc/01_FWx-PrecipTemp_compiled.csv", na = "NA")                 

```


# Data Summarization 

```{r samples count}

# filter for the six install sites for tidier calling
sixfilter <- sampleresults %>% filter(site == "Weeks-out" |
                                        site == "Leech-head" |
                                        site == "Chris-crk" |
                                        site == "Cragg-crk" |
                                        site == "West-Leech"| 
                                        site == "Tunnel") %>% 
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel")))


# how many of each sample_type are there at the 6 main sites?
# 324 samples overall
# 153 Grab (some ~30 duplicates) 
# 171 Rack
sixsites_samplecount_df <- sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab") %>%
  group_by(site, sample_type) %>%   
  summarise(number_of_samples = n()) 
# write_csv(sixsites_samplecount_df, path = "R-outputs_UBC-forWater-MSc_HMc/summ_sample-DOCcount.csv", na = "NA")  

# primary synoptic sampling sites (n > 1)
# 15 sites total
# 229 synoptic grab samples collected
synoptic_grabcount_df <- sampleresults %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab") %>%
  group_by(site = forcats::fct_explicit_na(site)) %>% 
  summarise(grab_sample_count = n()) %>% 
  filter(grab_sample_count > 1) %>% 
  mutate(what = "synoptic grab count")
# write_csv(synoptic_grabcount_df, path = "R-outputs_UBC-forWater-MSc_HMc/summ_synoptic-DOCcount-df.csv", na = "NA") 

# How many samples were collected overall
# 400 total
sample_count_df <- sampleresults %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab") %>%
  group_by(sample_type) %>% 
  summarise(sample_count = n()) %>% 
  mutate(what = "all analysed samples")
# write_csv(sample_count_df, path = "R-outputs_UBC-forWater-MSc_HMc/summ_allsamples-DOCcount-df.csv", na = "NA") 

# create a subset dataframe for the synoptically sampled sites 
# see 'snoptic_grabcount_df)
synopticfilter <- sampleresults %>% filter(site == "West-Leech"|
                                             site == "Tunnel"|
                                             site == "Cragg-crk"|
                                             site == "Leech-head"|
                                             site == "Weeks-out"|
                                             site == "Chris-crk"|
                                             site == "Jarvis"|
                                             site == "Lazar"|
                                             site == "Rithet"|
                                             site == "Deception-res"|
                                             site == "West-Jordan"|
                                             site == "Leech-downstreamconf"|
                                             site == "Judge-crk"|
                                             site == "Deception-crk"|
                                             site == "Boneyard") %>% 
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel",
                                        "Leech-downstreamconf", "Boneyard", 
                                        "Deception-crk", "Judge-crk", "Rithet", "Lazar", "Jarvis", "West-Jordan")))

# How many synoptic site samples were collected overall
# 386 total
synoptic_count_df <- synopticfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab") %>%
  group_by(sample_type) %>% 
  summarise(sample_count = n()) %>% 
  mutate(what = "synoptic count (rack and grabs)")
# write_csv(synoptic_count_df, path = "R-outputs_UBC-forWater-MSc_HMc/synopticsamples-DOCcount-df.csv", na = "NA")

# ------
# 15 synoptic sites (including the install sites)
## 215 synoptic grab samples (44 outside of the six sites)
# 6 installation sites
## 324 samples were collected/analyzed at the 6 installation sites:
### 153 Grab (39 replicates/treatability) 
### 171 Rack
# an additional 18 grab samples were collected (synoptically) but as one-offs (totaling 229 grabs overall)
# in total 400 samples were collected and analyzed
# ------

```

# Data Visualization

Plot data.

## DOC overall

These are plots of DOC concentration over time and space.

```{r DOC plots}

# Boxplot with jitter scatter 
# site vs DOC
# wrap by sample type
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab" & sample == "Grab") %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~sample_type, ncol = 2, nrow = 1) +  
  labs(caption = "DOC concentration by sample type: grab samples (n = 153) and rising limb rack samples (n = 171)", x = "", y = "DOC (mg/L)")
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_boxplot-Grab-vs-Rack.png") 


# Boxplot with jitter scatter 
# site vs DOC 
# grab and rack combined
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab" | sample_type == "Rack") %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none") +
  labs(caption = "DOC concentration across six sites over 15 months (324 samples)", x = "", y = "DOC (mg/L)")
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_boxplot-alltogether.png")


# density ridge 
# wrap by sample_type
# Grab: n = 114
# Rack: n = 171
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab" & sample == "Grab") %>%
  ggplot(aes(x = NPOC_ppm, y = fct_rev(site))) +
  ggridges::geom_density_ridges(aes(fill = site), alpha = 0.4) +
  facet_wrap(~sample_type, ncol = 1, nrow = 2) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  labs(y = "", x = "DOC (mg/L)", 
       caption = "Density distribution plots of DOC concentration at six sites based on sampling method (Grab: n = 153, Rack: n = 171)") +
  theme(legend.position = "none") 
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_ridgeplot_GvsR.png")


```

### Plots of DOC concentration by season 

```{r seasonal DOC plots}

# Boxplot with jitter scatter (DOC by season)
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab" & sample == "Grab") %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~two_seasons, ncol = 2, nrow = 1) +  
  labs(caption = "DOC concentration by season (dry: n = 45, wet: n = 240)", 
       x = "", y = "DOC (mg/L)")
# ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_boxplot-seasonal.png") 


# ----- Boxplots - Grab only with Sooke Tribs
# Boxplot with jitter scatter 
sampleresults %>% 
  dplyr::filter(site == "Weeks-out" |
                  site == "Leech-head" |
                  site == "Chris-crk" |
                  site == "Cragg-crk" |
                  site == "West-Leech"| 
                  site == "Tunnel" |
                  site == "Rithet" |
                  site == "Judge-crk", 
                analysis == "DOC", 
                sample_type == "Grab" & sample == "Grab") %>% 
  mutate(site = factor(site, 
                       levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel", "Rithet", "Judge-crk"))) %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~two_seasons, ncol = 2, nrow = 1) +  
  labs(caption = "DOC concentrations in the Leech and two main tribs to the Sooke Reservoir", 
       x = "", y = "DOC (mg/L)")
# ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_boxplot-seasonalwithSooketribs.png") 


# density ridge plots (facet wrap by season)
sixfilter %>% 
  dplyr::filter(analysis == "DOC",
                sample_type == "Rack" | sample_type == "Grab" & sample == "Grab") %>%
  ggplot(aes(x = NPOC_ppm, y = fct_rev(site))) +
  ggridges::geom_density_ridges(aes(fill = site), alpha = 0.4) +
  facet_wrap(~two_seasons, ncol = 1, nrow = 2) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  labs(y = "", x = "DOC (mg/L)", 
       caption = "Density distribution plots of DOC concentration by season (dry: n = 45, wet: n = 240)") +
  theme(legend.position = "none") 
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_ridgeplot-seasonal.png") 


# --- DOC scatter plot ---

# DOC over time all 6 sites in the Leech together
synopticfilter %>% 
  dplyr::filter(analysis == "DOC",
                sample_type == "Grab" | sample_type == "Rack") %>%
  mutate(trip_end = factor(trip_end)) %>% 
  ggplot(aes(x = trip_end, y = NPOC_ppm)) + 
  geom_jitter(aes(fill = sample_type), size = 2, shape = 22, alpha = 0.7) +
  scale_fill_manual(values = c("#09A4D2", "#f4AB0E")) +
  theme_bw() +
  labs(y = "DOC (mg/L)", x = "", fill = "sample type",
       caption = "DOC over fifteen months (Oct 2018-Jan 2020) from 386 synoptic samples (grab samples and vertical rack collection") +
  theme(axis.text.x = element_text(angle = 90), legend.position = "top")
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_scatter-total-sampletype.png") 

# at each of the six sites (DOC over time)
sixfilter %>% 
  dplyr::filter(analysis == "DOC",
                sample_type == "Rack" | sample_type == "Grab") %>%
  mutate(trip = factor(trip)) %>% 
  ggplot(aes(x = trip, y = NPOC_ppm)) +
  geom_jitter(aes(fill = sample_type), size = 2, shape = 21, alpha = 0.6) +
  scale_fill_manual(values = c("#f4AB0E", "#09A4D2")) +
  theme_bw() +
  labs(y = "DOC (mg/L)", x = "", fill = "sample type:") +
  facet_wrap(~site, ncol = 2, nrow = 3) +
  theme(axis.text.x = element_blank(), legend.position = "top")
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_facet-scatter-sampletype.png") 


# --- DOC facet wrap scatter plots ---
# I don't think these are good graphics
# Scatter main sites including sooke tribs
sampleresults %>% 
  dplyr::filter(site == "Weeks-out" |
                  site == "Leech-head" |
                  site == "Chris-crk" |
                  site == "Cragg-crk" |
                  site == "West-Leech"| 
                  site == "Tunnel" |
                  site == "Rithet" |
                  site == "Judge-crk", 
                analysis == "DOC", 
                sample_type == "Grab" & sample == "Grab") %>% 
  mutate(site = factor(site, 
                       levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel", "Rithet", "Judge-crk"))) %>% 
  ggplot(aes(x = dt_sampled, y = NPOC_ppm, fill = sample_type)) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21, size = 3) +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(caption = "DOC concentrations", x = "", y = "DOC (mg/L, as NPOC)") +
  theme(axis.text.x = element_text(angle = 90), legend.position = "none") +
  facet_wrap(~site, ncol = 2, nrow = 4)
# this is not a useful plot

```


### Plots of DOC & proxy

DOC was quantified as non-purgeable organic carbon on the Shimadzu TOC autoanalyzer, and samples were also measured on a Spectrolyser spectrophotometer. 
The spectrophotometer can only measure the fraction of organic matter that is able to absorb UV or Visible light (C-DOM), and therefore DOC measured on the Spectrolyser is a proxy measure of aromaticity (character).

```{r DOC conc and C-DOM}

# --- Spectrolyser data with TOCV data --- #
sampleresults %>% 
  filter(sample_type == "Grab" & sample == "Grab") %>% 
  summarise(n = n())
# all sites: DOC vs CDOM
sampleresults %>% 
  filter(sample_type == "Grab" & sample == "Grab") %>%
  mutate(site = factor(site, exclude = "Lab"),
         site = factor(site)) %>% 
  ggplot(aes(x = NPOC_ppm, y = DOCeq_ppm, fill = two_seasons)) +  
  geom_point(shape = 21, size = 3, alpha = 0.6) +
  geom_abline(lty = "dotted", slope = 1, intercept = 0) +
  scale_fill_manual(values = c("#f4AB0E", "#09A4D2")) +
  theme_bw() +
  xlim(NA, 20) +
  theme(legend.position = "top") +
  labs(x = "DOC (mg/L as NPOC)", y = "CDOM (mg/L from UV-Vis) ", fill = "sampling season:",
       caption = "Grab samples (n = 194) DOC concentrations from direct measure (as NPOC) and from UV-Vis absorbance (C-DOM, or spectral DOM-equivalent)") 
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC-CDOM_scatter-sampletype.png") 

# six primary sites: DOC vs CDOM
sixfilter %>% filter(analysis == "DOC") %>%
  ggplot(aes(x = NPOC_ppm, y = DOCeq_ppm, fill = two_seasons)) +
  geom_point(shape = 21, size = 2) +
  geom_abline(lty = "dotted", slope = 1, intercept = 0) +
  scale_fill_manual(values = c("#f4AB0E", "#09A4D2")) +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  theme_bw() +
  theme(legend.position = "top") +
  labs(x = "DOC (mg/L as NPOC)", y = "CDOM (mg/L from UV-Vis)", fill = "sampling season:",
       caption = "Grab sample DOC concentration based on direct (combustion measuring all non-purgeable organic carbon) and proxy (spectrophotometry measuring chromophoric fraction) methods of quantification show seasonal disparity. ...")

# SUVA vs time
sampleresults %>% 
  filter(sample_type == "Rack" | sample_type == "Grab" & sample == "Grab") %>%
  mutate(site = factor(site, exclude = "Lab"),
         site = factor(site),
         trip_end = factor(trip_end)) %>% 
  ggplot(aes(x = trip_end, y = SUVA, fill = two_seasons)) +  
  geom_jitter(shape = 21, size = 3, alpha = 0.6) +
  scale_fill_manual(values = c("#f4AB0E", "#09A4D2")) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "DOC (mg/L as NPOC)", y = "SUVA", fill = "sampling season:",
       caption = "Grab sample spectral concentrations (via spectrophotometry)...")



# ------ neat

# --- UV-Vis parameters
# --- Spectrolyser data with TOCV data
seasonal_wideresults %>% 
  filter(sample_type == "Grab" & sample == "Grab",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = NPOC_ppm, y = NO3.Neq_ppm, fill = season)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  geom_abline(lty = "dotted", slope = 1, intercept = 0) +
  scale_fill_manual(values = c("#5B99CC", "#3B3838", "#f4AB0E")) +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "C-DOM (proxy DOC, mg/L)", y = "nitrate (mg/L)", fill = "sampling season:",
       caption = "Grab sample DOC and nitrate concentrations (via spectrophotometry)...")

# --- Spectrolyser data - SAC254_Abs.m vs SAC436_Abs.m
seasonal_wideresults %>% 
  filter(sample_type == "Grab" & sample == "Grab",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = SAC254_Abs.m, y = SAC436_Abs.m, fill = season)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  geom_abline(lty = "dotted", slope = 1, intercept = 0) +
  scale_fill_manual(values = c("#5B99CC", "#3B3838", "#f4AB0E")) +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "SAC254_Abs.m", y = "SAC436_Abs.m", fill = "sampling season:",
       caption = "Grab sample spectral concentrations (via spectrophotometry)...")

# --- Spectrolyser data - NPOC vs SAC254_Abs.m
seasonal_wideresults %>% 
  filter(sample_type == "Grab" & sample == "Grab",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = NPOC_ppm, y = SAC254_Abs.m, fill = season)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = c("#5B99CC", "#3B3838", "#f4AB0E")) +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "DOC (mg/L as NPOC)", y = "CDOM abs (SAC 254 /m)", fill = "sampling season:",
       caption = "Grab sample spectral concentrations (via spectrophotometry)...")



# all sites DOC versus SAC 254
seasonal_wideresults %>% 
  filter(sample_type == "Grab" & sample == "Grab") %>%
  ggplot(aes(x = NPOC_ppm, y = SAC254_Abs.m, fill = season)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = c("#5B99CC", "#3B3838", "#f4AB0E")) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "DOC (mg/L as NPOC)", y = "CDOM abs (SAC 254 /m)", fill = "sampling season:",
       caption = "Grab sample spectral concentrations (via spectrophotometry)...")


# --- RACK SAMPLES

#install.packages("viridis")
library(viridis)

# --- DOC versus CDOM on rack samples
sampleresults_wide %>% 
  filter(sample_type == "Rack",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = NPOC_ppm, y = DOCeq_ppm, fill = sample)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  theme_bw() +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  viridis::scale_fill_viridis(discrete = TRUE) 
labs(x = "DOC (mg/L as NPOC)", y = "CDOM (mg/L)", fill = "Rack Position:",
     caption = "Rack sample DOC concentration based on direct (combustion measuring all non-purgeable organic carbon) and proxy (spectrophotometry measuring chromophoric fraction) methods of quantification...")

# --- DOC versus NO3- on rack samples
sampleresults_wide %>% 
  filter(sample_type == "Rack",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = NPOC_ppm, y = NO3.Neq_ppm, fill = sample)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  theme_bw() +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(x = "DOC (mg/L as NPOC)", y = "nitrate (mg/L)", fill = "Rack Position:",
       caption = "Rack sample DOC and nitrate concentrations (via spectrophotometry)...")

# --- facet wrap scatter plots of conc --- ## W.I.P. ###
# DOC over time (by trip) -- try mutating in a month-year for clarity
sampleresults_wide %>% 
  dplyr::filter(sample_type == "Rack",
                site == "Weeks-out" |
                  site == "Leech-head" |
                  site == "Chris-crk" |
                  site == "Cragg-crk" |
                  site == "West-Leech"| 
                  site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  mutate(trip = factor(trip, levels = (1:22))) %>% 
  ggplot(aes(x = trip, y = NPOC_ppm, fill = sample)) +
  geom_jitter(shape = 21, size = 2) +
  #facet_wrap(~site, ncol = 2, nrow = 3) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  #geom_jitter() +
  #theme_bw() +
  #labs(y = "DOC (mg/L)", x = "time span", colour = "sample type:") +
  #theme(legend.position = "top",
  # axis.text.x = element_text(angle = 90))   # rotate tick labels for clarity
  
  ```





### Plots of River stage (6 sites)

```{r stage plots}

# --- facet wrap scatter plots of river stage over time (hydrograph) ---
stage_df %>% 
  mutate(source = factor(source, levels = c("Weeks", "ChrisCrk", "LeechHead", "CraggCrk", "WestLeech",  "Tunnel"))) %>%
  mutate(interval = factor(interval, levels = (1:22))) %>% 
  ggplot(aes(x = DateTime, y = stage_cm)) + 
  geom_line(aes(colour = source)) +
  theme_bw() +
  labs(y = "stage (cm)", x = "") +
  facet_wrap(~source, ncol = 1) +
  theme(legend.position = "none")  

```
.
.
.
.
.


## the following code chunks and text are old (to be updated):


Import weather data to generate rapid-runoff plots.

```{r FWx.data OLD}

# read in csv file provided by CRD technologist
# combine separate files and update DateTime format to Posixct
# add a variable of rain in centimeters (stage is in cm)
wx_df <- rbind(
  read.csv(file = "R-inputs/CRD_FWx-Data/2019-04-16_Wx_CC-MG_Sept-Dec2018.csv", header = TRUE),
  read.csv(file = "R-inputs/CRD_FWx-Data/2019-04-16_FWxChris-Creek-trunc.csv", header = TRUE),
  read.csv(file = "R-inputs/CRD_FWx-Data/2019-04-16_FWxMartins-trunc.csv", header = TRUE)) %>% 
  mutate(DateTime = lubridate::ymd_hm(DateTime, tz = TZ), 
         Rn_cm = Rn_mm/10)

str(wx_df)


# Plot Precip from CRD fire weather (FWx) stations

# FWx Chris Creek  
plot_wx_CC <- wx_df %>% 
  filter(StationName == "FWx Chris Creek") %>% 
  ggplot(aes(x = DateTime, y = Rn_cm)) +
  geom_bar(stat = 'identity', fill = forWater_colours[1]) +
  theme_light() +
  labs(y = "Rain (cm)", subtitle = "Chris Creek Wx-Stn") +
  scale_y_reverse()
plot_wx_CC

# FWx Martins Gulch
plot_wx_MG <- wx_df %>% 
  filter(StationName == "FWx Martins Gulch") %>% 
  ggplot(aes(x = DateTime, y = Rn_cm)) +
  geom_bar(stat = 'identity', fill = forWater_colours[1]) +
  theme_light() +
  labs(y = "Rain (cm)", subtitle = "Martins Gulch Wx-Stn") +
  scale_y_reverse()
plot_wx_MG

# set these up for rapid runoff plots later
gpt_wx_CC <- ggplot_gtable(ggplot_build(plot_wx_CC))
gpt_wx_MG <- ggplot_gtable(ggplot_build(plot_wx_MG))


## old code...
# ----------------
## I don't think I need this now -- use 'group_by' or 'filter()' 
# subset into two dataframes for headwaters and reach sites (Chris Creek Wx-stn and Martin's Gulch Wx-stn)
# subset the weather data to match stage data
# Chris Crk Wx-stn (headwaters)
#wx_CC <- subset(wx_df_full, (StationName == "FWx Chris Creek") 
#                & (DateTime >= "2018-10-26 10:00") 
#                & (DateTime <= "2019-04-11 13:00"))  
# Martin's Gulch Wx-stn (Lower reach)
#wx_MG <- subset(wx_df_full, (StationName == "FWx Martins Gulch") 
#                & (DateTime >= "2018-10-26 10:00") 
#                & (DateTime <= "2019-04-11 13:00"))  

# convert rain in mm to cm for comparison to stage rise
#wx_CC$precip.cm <- wx_CC$Rn_mm/10
#wx_MG$precip.cm <- wx_MG$Rn_mm/10

#head(wx_CC)
#head(wx_MG)


# Leech River Tunnel site was installed late
# subset the weather data to match the Tunnel stage data span
#wx_CC_tunnelspan <- subset(wx_df_full, (StationName == "FWx Chris Creek") 
#                           & (DateTime >= "2018-12-07 01:00") 
#                           & (DateTime <= "2019-04-11 13:00"))  
# Martin's Gulch Wx-stn (Lower reach)
#wx_MG_tunnelspan <- subset(wx_df_full, (StationName == "FWx Martins Gulch") 
#                           & (DateTime >= "2018-12-07 01:00") 
#                           & (DateTime <= "2019-04-11 13:00"))  


# ------------ REMOVE?
# special plotting case for Tunnel (late install, different subset with shorter time span)

# FWx_Chris_Creek
#plot_wx_CC_tunnelspan <- ggplot(wx_CC_tunnelspan, aes(DateTime, precip.cm)) +
#  geom_bar(stat = 'identity', fill = forWater_colours[3]) +
#  theme_minimal() +
#  theme(panel.grid = element_blank(), 
#        panel.background = element_blank(),
#        axis.ticks = element_blank(),
#        axis.title.x   = element_blank(),
#        axis.ticks.x    = element_blank()) +
#  ylab("Rain (cm)") +
#  labs(subtitle = "Chris Creek Wx-Stn") +
#  scale_y_reverse()
#plot_wx_CC_tunnelspan

# FWx_Martins_Gulch
#plot_wx_MG_tunnelspan <- ggplot(wx_MG_tunnelspan, aes(DateTime, precip.cm)) +
#  geom_bar(stat = 'identity', fill = forWater_colours[3]) +
#  theme_minimal() +
#  theme(panel.grid = element_blank(), 
#        panel.background = element_blank(),
#        axis.ticks = element_blank(),
#        axis.title.x   = element_blank(),
#        axis.ticks.x    = element_blank()) +
#  ylab("Rain (cm)") +
#  labs(subtitle = "Martin's Gulch Wx-Stn") +
#  scale_y_reverse()
#plot_wx_MG_tunnelspan

# set these up for rainfall-level plots (rapid runoff plot)
#gpt_wx_CC_tunnelspan <- ggplot_gtable(ggplot_build(plot_wx_CC_tunnelspan))
#gpt_wx_MG_tunnelspan <- ggplot_gtable(ggplot_build(plot_wx_MG_tunnelspan))

```

Bring in stage data from Odyssey capacitance water level loggers. Each site has multiple data blocks. Watch for alternating formats of dates.


Make hydrographs with stage (desire is to obtain Q)

```{r hydrographs_1}
setwd("C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/")

# run a loop to plot stage for each site
# save each stage plot in a list to call later
stagePlots_list <- vector("list", 6)

# vector to call text format for plots
plottextformat <- element_text(size = 14, colour = forWater_colours[4])

# save a theme vector to add to each plot
stageplottheme <- theme_bw() + 
  theme(legend.title = plottextformat,
        legend.text = plottextformat,
        axis.title = plottextformat,
        axis.text = plottextformat,
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(colour = forWater_colours[4]))

# chose the colour you want
forWater_col <- forWater_colours[3]

# loop for sites 1-5
for (i in seq_along(site_names[1:5])) {
  s <- ggplot(filter(stage.event_dfSS5, site == site_names[i]), aes(x = DateTime, y = Stage_cm)) + 
    geom_point(col = forWater_col) + 
    stageplottheme +
    labs(x = "", y = "Stage (cm)", caption = site_captions[i])
  
  stagePlots_list[[i]] <- s  # save plot to list for calls later (in order of 'site_names')
  ggsave(filename = paste("Stage_Plot_",i,"_",site_names[i],".png"), s)
}

# plot the tunnel separately becasue it has a truncated stage df
s <- ggplot(filter(stage.event_dfSS5, site == site_names[6]), aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  stageplottheme +
  labs(x = "", y = "Stage (cm)", caption = site_captions[6])
stagePlots_list[[6]] <- s  # save plot to list for calls later (in order of 'site_names')
ggsave(filename = paste("Stage_Plot_",6,"_",site_names[6],".png"), s)

# rename the stage plot list elements
names(stagePlots_list) <- paste(site_names,"stage")

```

it didn't work to save my graphs in a vector so here they are again, less janky but not totally elegant

```{r hydrographs_2}
setwd("C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/")

# set up fresh hydrographs (currently in Janky Shit)
# note: "ggplot_gtable" sets up the plot to be used in grid layout for rapidrunoff plots

# vector to call text format for plots
plottextformat <- element_text(size = 14, colour = forWater_colours[4])

# save a theme vector to add to each plot
stageplottheme <- theme_bw() + 
  theme(legend.title = plottextformat,
        legend.text = plottextformat,
        axis.title = plottextformat,
        axis.text = plottextformat,
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(colour = forWater_colours[4]))

# chose the colour you want
forWater_col <- forWater_colours[3]

# ::: Weeks Outlet 
plot_wks_stg <- 
  ggplot(filter(stage.event_dfSS5, site == site_names[1]), aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  stageplottheme +
  labs(x = "", y = "Stage (cm)", caption = site_captions[i])
ggsave(filename = paste("Stage_Plot_",1,"_",site_names[1],".png"))

gtb_wks_stg <- ggplot_gtable(ggplot_build(plot_wks_stg))  


# :: Leech River Head 
plot_L.head_stg <- 
  ggplot(filter(stage.event_dfSS5, site == site_names[2]), aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  stageplottheme +
  labs(x = "", y = "Stage (cm)", caption = site_captions[i])
ggsave(filename = paste("Stage_Plot_",2,"_",site_names[2],".png"))

gtb_L.head_stg <- ggplot_gtable(ggplot_build(plot_L.head_stg))


# :: Chris Creek 
plot_chris_stg <- 
  ggplot(filter(stage.event_dfSS5, site == site_names[3]), aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  stageplottheme +
  labs(x = "", y = "Stage (cm)", caption = site_captions[i])
ggsave(filename = paste("Stage_Plot_",3,"_",site_names[3],".png"))

gtb_chris_stg <- ggplot_gtable(ggplot_build(plot_chris_stg))


# :: Cragg Creek 
plot_cragg_stg <- 
  ggplot(filter(stage.event_dfSS5, site == site_names[4]), aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  stageplottheme +
  labs(x = "", y = "Stage (cm)", caption = site_captions[i])
ggsave(filename = paste("Stage_Plot_",4,"_",site_names[4],".png"))

gtb_cragg_stg <- ggplot_gtable(ggplot_build(plot_cragg_stg))


# :: West Leech River 
plot_west_stg <- 
  ggplot(filter(stage.event_dfSS5, site == site_names[5]), aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  stageplottheme +
  labs(x = "", y = "Stage (cm)", caption = site_captions[i])
ggsave(filename = paste("Stage_Plot_",5,"_",site_names[5],".png"))

gtb_west_stg <- ggplot_gtable(ggplot_build(plot_west_stg))


# :: Tunnel
plot_tunnel_stg <-
  ggplot(filter(stage.event_dfSS6, site == site_names[6]), aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  stageplottheme +
  labs(x = "", y = "Stage (cm)", caption = site_captions[i])
ggsave(filename = paste("Stage_Plot_",6,"_",site_names[6],".png"))

gtb_tunnel_stg <- ggplot_gtable(ggplot_build(plot_tunnel_stg))
```


#Goal:match bottle height to logged stage

1. read in data files with NPOC concentrations, dates bottles were set and collected, and fill stage (or grab sample dates)
2. read in stage data from Odyssey Capacitance water level loggers
3. fix dates, add identifying/grouping columns for SITE & EVENT
4. filter by site & event & analysis (DOC)
5. match samples to logged stage and extract matching date-time 
6. add DateTime stamps to sample results dataframes

Note: in the future it might be tidier to keep grab samples and rack samples results in one file & one dataframe. They can be easily grouped. For now, we'll keep them separate (gotta make a poster).

Plot the DOC results on each hydrograph

Weeks Outlet (Drainage from Jordan Meadows)

I think you can do thins in a loop with i as the seq_along(site_names[i]) and j as the seq_along(event[j]) 
call vector of events for trip_df

```{r OC+stage_wks}
# --- wks 1
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[1] & event == "1") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[1] & event == "1") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

wks_ev1_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- wks 2
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[1] & event == "2") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[1] & event == "2") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

wks_ev2_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- wks 3
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[1] & event == "3") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[1] & event == "3") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

wks_ev3_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- wks 4
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[1] & event == "4") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[1] & event == "4") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

wks_ev4_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #



# --- wks 5
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[1] & event == "5") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[1] & event == "5") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

wks_ev5_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #
## Event five - freezing event. L1 was recorded as being set at 91 cm but the stage was not recorded as getting that high...


# --- wks 6
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[1] & event == "6") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[1] & event == "6") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)
# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

wks_ev6_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #

## -- This could be improved - possibly with a case_when() or a loop or apply?? --- #


# combine all events into one weeks-df
# no fifth -- wks_matched <- rbind(wks_ev1_df,wks_ev2_df, wks_ev3_df, wks_ev4_df, wks_ev5_df, wks_ev6_df)
wks_matched <- rbind(wks_ev1_df,wks_ev2_df, wks_ev3_df, wks_ev4_df, wks_ev5_df, wks_ev6_df)



# --- make a plot --- #
# find the start of each visit
# use these to add vertical lines to stage plots (for your guidance)
visits <- stage.event_df %>%
  group_by(event) %>% 
  summarise(date = first(DateTime)) %>% 
  ungroup()
visits <- visits[,2]
visits <- visits[[1]]
last_visit <- (last(stage.event_df$DateTime)) 


# vector for visit line colours 
visit_col <- forWater_colours[5]
# rack sample points
point_col <- forWater_colours[5]
# grab colour
grab_col <- forWater_colours[4]


# --- INPUTS --- #
Site.Name <- site_names[1]
rackDOC <- wks_matched
stg_DOCplot <- plot_wks_stg

# grab data (site name)
grabDOC <- grabs_df %>% 
  filter(analysis == "DOC" & Site == site_names[1]) %>% 
  select(Site, sample, filling.stage.cm, Grab_DateTime, Result)
# --- --- --- --- #

# --- get fancy --- #

site.visit.plot <- 
  stg_DOCplot +
  #geom_vline(xintercept = visits[1:6], linetype = "solid", colour = visit_col, size = 0.7) + 
  #geom_vline(xintercept = last_visit, linetype = "solid", colour = visit_col, size = 0.7) +
  geom_point(data = grabDOC, aes(x = Grab_DateTime, y = filling.stage.cm, size = 4), colour = grab_col, show.legend = FALSE) +
  geom_point(data = rackDOC, aes(x = sample_time, y = sample_stage, size = 4), colour = point_col, show.legend = FALSE) 
site.visit.plot 


# save as a picture
ggsave(paste("sample-hydrgr_", Site.Name, ".png"), plot = site.visit.plot, 
       path = "C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/",
       width = 7.29, height = 4.5, units = "in")

# --- fancy --- #

# set up for combo plot (rainfall-streamflow)
gpt_wks_samp <- ggplot_gtable(ggplot_build(site.visit.plot))

```

# Leech River Head

```{r OC-stage_leech-head}

# --- Leech-Head 1
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[2] & event == "1") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[2] & event == "1") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

L.Head_ev1_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- LHead 2
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[2] & event == "2") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[2] & event == "2") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

L.Head_ev2_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- L.Head 3
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[2] & event == "3") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[2] & event == "3") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

L.Head_ev3_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- L.Head 4
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[2] & event == "4") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[2] & event == "4") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

L.Head_ev4_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- L.Head 5
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[2] & event == "5") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[2] & event == "5") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

L.Head_ev5_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- L.Head 6
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[2] & event == "6") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[2] & event == "6") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

L.Head_ev6_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# combine all events into one weeks-df
L.Head_matched <- rbind(L.Head_ev1_df,L.Head_ev2_df, L.Head_ev3_df, L.Head_ev4_df, L.Head_ev5_df, L.Head_ev6_df)


# --- make a plot --- #
# find the start of each visit
# use these to add vertical lines to stage plots (for your guidance)
visits <- stage.event_df %>%
  group_by(event) %>% 
  summarise(date = first(DateTime)) %>% 
  ungroup()
visits <- visits[,2]
visits <- visits[[1]]
last_visit <- (last(stage.event_df$DateTime)) 


# vector for visit line colours 
visit_col <- forWater_colours[5]
# rack sample points
point_col <- forWater_colours[5]
# grab colour
grab_col <- forWater_colours[4]


# --- INPUTS --- #
Site.Name <- site_names[2]
rackDOC <- L.Head_matched
stg_DOCplot <- plot_L.head_stg

# grab data (site name)
grabDOC <- grabs_df %>% 
  filter(analysis == "DOC" & Site == site_names[2]) %>% 
  select(Site, sample, filling.stage.cm, Grab_DateTime, Result)
# --- --- --- --- #

# --- get fancy --- #

site.visit.plot <- 
  stg_DOCplot +
  #geom_vline(xintercept = visits[1:6], linetype = "solid", colour = visit_col, size = 0.7) + 
  #geom_vline(xintercept = last_visit, linetype = "solid", colour = visit_col, size = 0.7) +
  geom_point(data = grabDOC, aes(x = Grab_DateTime, y = filling.stage.cm, size = 4), colour = grab_col, show.legend = FALSE) +
  geom_point(data = rackDOC, aes(x = sample_time, y = sample_stage, size = 4), colour = point_col, show.legend = FALSE) 
site.visit.plot 

# save as a picture
ggsave(paste("sample-hydrgr_", Site.Name, ".png"), plot = site.visit.plot, 
       path = "C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/",
       width = 7.29, height = 4.5, units = "in")

# --- fancy --- #

# set up for combo plot (rainfall-streamflow)
gpt_LHead_samp <- ggplot_gtable(ggplot_build(site.visit.plot))
```

# Chris Creek

```{r OC-stage_chris-creek}

# --- Chriscrk 1
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[3] & event == "1") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[3] & event == "1") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

Chriscrk_ev1_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- Chriscrk 2
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[3] & event == "2") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[3] & event == "2") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

Chriscrk_ev2_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- Chriscrk 3
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[3] & event == "3") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[3] & event == "3") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)
# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

Chriscrk_ev3_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- Chriscrk 4
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[3] & event == "4") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[3] & event == "4") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

Chriscrk_ev4_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- Chriscrk 5
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[3] & event == "5") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[3] & event == "5") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

Chriscrk_ev5_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- Chriscrk 6
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[3] & event == "6") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[3] & event == "6") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

Chriscrk_ev6_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #

# combine all events into one weeks-df
Chriscrk_matched <- rbind(Chriscrk_ev1_df, Chriscrk_ev2_df, Chriscrk_ev3_df, Chriscrk_ev4_df, Chriscrk_ev5_df, Chriscrk_ev6_df)

# --- make a plot --- #
# find the start of each visit
# use these to add vertical lines to stage plots (for your guidance)
visits <- stage.event_df %>%
  group_by(event) %>% 
  summarise(date = first(DateTime)) %>% 
  ungroup()
visits <- visits[,2]
visits <- visits[[1]]
last_visit <- (last(stage.event_df$DateTime)) 

# vector for visit line colours 
visit_col <- forWater_colours[5]
# rack sample points
point_col <- forWater_colours[5]
# grab colour
grab_col <- forWater_colours[4]


# --- INPUTS --- #
Site.Name <- site_names[3]
rackDOC <- Chriscrk_matched
stg_DOCplot <- plot_chris_stg

# grab data (site name)
grabDOC <- grabs_df %>% 
  filter(analysis == "DOC" & Site == site_names[3]) %>% 
  select(Site, sample, filling.stage.cm, Grab_DateTime, Result)
# --- --- --- --- #

# --- get fancy --- #

site.visit.plot <- 
  stg_DOCplot +
  #geom_vline(xintercept = visits[1:6], linetype = "solid", colour = visit_col, size = 0.7) + 
  #geom_vline(xintercept = last_visit, linetype = "solid", colour = visit_col, size = 0.7) +
  geom_point(data = grabDOC, aes(x = Grab_DateTime, y = filling.stage.cm, size = 4), colour = grab_col, show.legend = FALSE) +
  geom_point(data = rackDOC, aes(x = sample_time, y = sample_stage, size = 4), colour = point_col, show.legend = FALSE) 
site.visit.plot 

# save as a picture
ggsave(paste("sample-hydrgr_", Site.Name, ".png"), plot = site.visit.plot, 
       path = "C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/",
       width = 7.29, height = 4.5, units = "in")

# --- fancy --- #

# set up for combo plot (rainfall-streamflow)
gpt_Crscrk_samp <- ggplot_gtable(ggplot_build(site.visit.plot))
```

# Cragg Creek

```{r OC-stage_cragg}

# --- cragg 1
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[4] & event == "1") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[4] & event == "1") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

cragg_ev1_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- cragg 2
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[4] & event == "2") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[4] & event == "2") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

cragg_ev2_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- cragg 3
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[4] & event == "3") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[4] & event == "3") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)
# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

cragg_ev3_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- cragg 4
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[4] & event == "4") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[4] & event == "4") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

cragg_ev4_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- cragg 5
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[4] & event == "5") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[4] & event == "5") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

cragg_ev5_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- cragg 6
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[4] & event == "6") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[4] & event == "6") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

cragg_ev6_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #

# combine all events into one weeks-df
# no fifth -- wks_matched <- rbind(wks_ev1_df,wks_ev2_df, wks_ev3_df, wks_ev4_df, wks_ev5_df, wks_ev6_df)
cragg_matched <- rbind(cragg_ev1_df, cragg_ev2_df, cragg_ev3_df, cragg_ev4_df, cragg_ev5_df, cragg_ev6_df)

# --- make a plot --- #
# find the start of each visit
# use these to add vertical lines to stage plots (for your guidance)
visits <- stage.event_df %>%
  group_by(event) %>% 
  summarise(date = first(DateTime)) %>% 
  ungroup()
visits <- visits[,2]
visits <- visits[[1]]
last_visit <- (last(stage.event_df$DateTime)) 

# vector for visit line colours 
visit_col <- forWater_colours[5]
# rack sample points
point_col <- forWater_colours[5]
# grab colour
grab_col <- forWater_colours[4]


# --- INPUTS --- #
Site.Name <- site_names[4]
rackDOC <- cragg_matched
stg_DOCplot <- plot_cragg_stg

# grab data (site name)
grabDOC <- grabs_df %>% 
  filter(analysis == "DOC" & Site == site_names[4]) %>% 
  select(Site, sample, filling.stage.cm, Grab_DateTime, Result)
# --- --- --- --- #

# --- get fancy --- #
site.visit.plot <- 
  stg_DOCplot +
  #geom_vline(xintercept = visits[1:6], linetype = "solid", colour = visit_col, size = 0.7) + 
  #geom_vline(xintercept = last_visit, linetype = "solid", colour = visit_col, size = 0.7) +
  geom_point(data = grabDOC, aes(x = Grab_DateTime, y = filling.stage.cm, size = 4), colour = grab_col, show.legend = FALSE) +
  geom_point(data = rackDOC, aes(x = sample_time, y = sample_stage, size = 4), colour = point_col, show.legend = FALSE) 
site.visit.plot 

# save as a picture
ggsave(paste("sample-hydrgr_", Site.Name, ".png"), plot = site.visit.plot, 
       path = "C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/",
       width = 7.29, height = 4.5, units = "in")

# --- fancy --- #

# set up for combo plot (rainfall-streamflow)
gpt_Craggcrk_samp <- ggplot_gtable(ggplot_build(site.visit.plot))
```

# West Leech River

```{r OC-stage_west}

# --- west 1
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[5] & event == "1") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[5] & event == "1") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

west_ev1_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- west 2
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[5] & event == "2") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[5] & event == "2") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

west_ev2_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- west 3
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[5] & event == "3") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[5] & event == "3") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)
# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

west_ev3_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- west 4
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[5] & event == "4") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[5] & event == "4") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

west_ev4_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- west 5
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[5] & event == "5") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[5] & event == "5") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

west_ev5_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- west 6
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[5] & event == "6") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[5] & event == "6") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

west_ev6_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #

# combine all events into one weeks-df
west_matched <- rbind(west_ev1_df, west_ev2_df, west_ev3_df, west_ev4_df, west_ev5_df, west_ev6_df)

# --- make a plot --- #
# find the start of each visit
# use these to add vertical lines to stage plots (for your guidance)
visits <- stage.event_df %>%
  group_by(event) %>% 
  summarise(date = first(DateTime)) %>% 
  ungroup()
visits <- visits[,2]
visits <- visits[[1]]
last_visit <- (last(stage.event_df$DateTime)) 

# vector for visit line colours 
visit_col <- forWater_colours[5]
# rack sample points
point_col <- forWater_colours[5]
# grab colour
grab_col <- forWater_colours[4]


# --- INPUTS --- #
Site.Name <- site_names[5]
rackDOC <- west_matched
stg_DOCplot <- plot_west_stg

# grab data (site name)
grabDOC <- grabs_df %>% 
  filter(analysis == "DOC" & Site == site_names[5]) %>% 
  select(Site, sample, filling.stage.cm, Grab_DateTime, Result)
# --- --- --- --- #

# --- get fancy --- #
site.visit.plot <- 
  stg_DOCplot +
  #geom_vline(xintercept = visits[1:6], linetype = "solid", colour = visit_col, size = 0.7) + 
  #geom_vline(xintercept = last_visit, linetype = "solid", colour = visit_col, size = 0.7) +
  geom_point(data = grabDOC, aes(x = Grab_DateTime, y = filling.stage.cm, size = 4), colour = grab_col, show.legend = FALSE) +
  geom_point(data = rackDOC, aes(x = sample_time, y = sample_stage, size = 4), colour = point_col, show.legend = FALSE) 
site.visit.plot 

# save as a picture
ggsave(paste("sample-hydrgr_", Site.Name, ".png"), plot = site.visit.plot, 
       path = "C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/",
       width = 7.29, height = 4.5, units = "in")

# --- fancy --- #

# set up for combo plot (rainfall-streamflow)
gpt_WestL_samp <- ggplot_gtable(ggplot_build(site.visit.plot))

```

# Leech River Tunnel

```{r OC-stage_tunnel}
# this site was installed late, in December
# event 1 for the tunnel was "event 3" for all others...


# --- tunnel 1 (3)
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[6] & event == "3") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[6] & event == "3") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

tunnel_ev1_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- tunnel 2 (4)
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[6] & event == "4") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[6] & event == "4") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

tunnel_ev2_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- tunnel 3 (5)
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[6] & event == "5") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[6] & event == "5") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)
# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

tunnel_ev3_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #


# --- tunnel 4 (6)
# --- INPUTS --- #
# create subset working dataframes 
stg_df <- filter(stage.event_df, site == site_names[6] & event == "6") %>% 
  select(event, site, DateTime, Stage_cm)

samp_df <- filter(racks_df, analysis == "DOC" & site == site_names[6] & event == "6") %>% 
  select(event, site, sample, Fill.Stage_cm, analysis, Result)

# --- OUTPUTS --- #
# defined based on your INPUT values (no need to alter)

# this is the stage date you're targeting (by site)
stg <- stg_df$Stage_cm
# this is the time series you're targeting
t.series <- stg_df$DateTime  
# this is the stage you need a date-time for
level <- samp_df$Fill.Stage_cm 

# assign empty vectors to hold the outputs from the loop
l <- length(samp_df$sample)
occur_fill <- vector(length = l)
stg_fill   <- vector(length = l)
time_fill  <- vector(length = l)

for (i in seq_along(samp_df$sample)) {
  occur_fill[i] <- detect_index(stg, ~ .x >= level[i], .right = FALSE)
  stg_fill[i] <- stg[occur_fill[i]]
} 

tunnel_ev4_df <- samp_df %>% 
  select(event, site, Fill.Stage_cm, analysis, Result) %>% 
  mutate(index = occur_fill, sample_stage = stg_fill, sample_time = t.series[occur_fill])
# --- #



# combine all events into one weeks-df
#west_ev3_df, west_ev4_df, 
tunnel_matched <- rbind(tunnel_ev1_df, tunnel_ev2_df, tunnel_ev3_df, tunnel_ev4_df)

# --- make a plot --- #
# find the start of each visit
# use these to add vertical lines to stage plots (for your guidance)
visits <- stage.event_df %>%
  group_by(event) %>% 
  summarise(date = first(DateTime)) %>% 
  ungroup()
visits <- visits[,2]
visits <- visits[[1]]
last_visit <- (last(stage.event_df$DateTime)) 

# vector for visit line colours 
visit_col <- forWater_colours[5]
# rack sample points
point_col <- forWater_colours[5]
# grab colour
grab_col <- forWater_colours[4]


# --- INPUTS --- #
Site.Name <- site_names[6]
rackDOC <- tunnel_matched
stg_DOCplot <- plot_tunnel_stg

# grab data (site name)
grabDOC <- grabs_df %>% 
  filter(analysis == "DOC" & Site == site_names[6]) %>% 
  select(Site, sample, filling.stage.cm, Grab_DateTime, Result)
# --- --- --- --- #

# --- get fancy --- #
site.visit.plot <- 
  stg_DOCplot +
  #geom_vline(xintercept = visits[1:6], linetype = "solid", colour = visit_col, size = 0.7) + 
  #geom_vline(xintercept = last_visit, linetype = "solid", colour = visit_col, size = 0.7) +
  geom_point(data = grabDOC, aes(x = Grab_DateTime, y = filling.stage.cm, size = 4), colour = grab_col, show.legend = FALSE) +
  geom_point(data = rackDOC, aes(x = sample_time, y = sample_stage, size = 4), colour = point_col, show.legend = FALSE) 
site.visit.plot 

# save as a picture
ggsave(paste("sample-hydrgr_", Site.Name, ".png"), plot = site.visit.plot, 
       path = "C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/",
       width = 7.29, height = 4.5, units = "in")


# --- fancy --- #

# set up for combo plot (rainfall-streamflow)
gpt_Tunnel_samp <- ggplot_gtable(ggplot_build(site.visit.plot))
```

# make rapid runoff plots with the sample hydrographs

```{r rainfall-runoff_sample_plots}
setwd("C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/")

# create rainfall and stream level plots and save each as an image

# Site 1 ------------------------------- 
# Weeks Lake Outlet 
# with CC-Wx 
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], 
                      gpt_wks_samp$widths[2:3])
gpt_wx_CC$widths[2:3] <- maxWidth
gpt_wks_samp$widths[2:3] <- maxWidth

rr_WksOut_CC <- grid.arrange(gpt_wx_CC, gpt_wks_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_WksOut-CC.png", rr_WksOut_CC)


# Site 2  ------------------------------- 
# Leech River Head (below colfluence of Chris and Weeks) 
# with CC-Wx
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], 
                      gpt_LHead_samp$widths[2:3])
gpt_wx_CC$widths[2:3] <- maxWidth
gpt_LHead_samp$widths[2:3] <- maxWidth

rr_LHead_CC <- grid.arrange(gpt_wx_CC, gpt_LHead_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_LHead-CC.png", rr_LHead_CC)


# Site 3  ------------------------------- 
# Chris Creek
# with CC-Wx 
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], gpt_Crscrk_samp$widths[2:3])
gpt_wx_CC$widths[2:3]  <- maxWidth
gpt_Crscrk_samp$widths[2:3] <- maxWidth

rr_chris_CC <- grid.arrange(gpt_wx_CC, gpt_Crscrk_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_chris-CC.png", rr_chris_CC)


# Site 4   ------------------------------- 
# Cragg Creek 
# with CC-Wx 
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], 
                      gpt_Craggcrk_samp$widths[2:3])
gpt_wx_CC$widths[2:3] <- maxWidth
gpt_Craggcrk_samp$widths[2:3] <- maxWidth

rr_cragg_CC <- grid.arrange(gpt_wx_CC, gpt_Craggcrk_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_cragg-CC.png", rr_cragg_CC)


# Cragg Creek
# with MG-Wx 
maxWidth <- unit.pmax(gpt_wx_MG$widths[2:3], 
                      gpt_Craggcrk_samp$widths[2:3])
gpt_wx_MG$widths[2:3] <- maxWidth
gpt_Craggcrk_samp$widths[2:3] <- maxWidth

rr_cragg_MG <- grid.arrange(gpt_wx_MG, gpt_Craggcrk_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_cragg-MG.png", rr_cragg_MG)


# Site 5  ------------------------------- 
# West Leech River 
# with MG-Wx
maxWidth <- unit.pmax(gpt_wx_MG$widths[2:3], 
                      gpt_WestL_samp$widths[2:3])
gpt_wx_MG$widths[2:3] <- maxWidth
gpt_WestL_samp$widths[2:3] <- maxWidth

rr_WLeech_MG <- grid.arrange(gpt_wx_MG, gpt_WestL_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_WLeech-MG.png", rr_WLeech_MG)


# West Leech River
# with CC-Wx
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], 
                      gpt_WestL_samp$widths[2:3])
gpt_wx_CC$widths[2:3] <- maxWidth
gpt_WestL_samp$widths[2:3] <- maxWidth

rr_WLeech_CC <- grid.arrange(gpt_wx_CC, gpt_WestL_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_WLeech-CC.png", rr_WLeech_CC)


# Site 6  ------------------------------- This one isn't lined up properly b/c late installation 
# Leech River Tunnel 
# with CC-Wx
maxWidth <- unit.pmax(gpt_wx_CC_tunnelspan$widths[2:3], 
                      gpt_Tunnel_samp$widths[2:3])
gpt_wx_CC_tunnelspan$widths[2:3] <- maxWidth
gpt_Tunnel_samp$widths[2:3] <- maxWidth

rr_Tunnel_CC <- grid.arrange(gpt_wx_CC_tunnelspan, gpt_Tunnel_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_Tunnel-CC.png", rr_Tunnel_CC)

# Leech River Tunnel 
# with MG-wx
maxWidth <- unit.pmax(gpt_wx_CC_tunnelspan$widths[2:3], 
                      gpt_Tunnel_samp$widths[2:3])
gpt_wx_MG_tunnelspan$widths[2:3] <- maxWidth
gpt_Tunnel_samp$widths[2:3] <- maxWidth

rr_Tunnel_MG <- grid.arrange(gpt_wx_MG_tunnelspan, gpt_Tunnel_samp, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-sampplot_Tunnel-MG.png", rr_Tunnel_MG)

```

# This is tidy and logical code :)
result is 'DOCresults_df'
```{r summary stats}
setwd("C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/")
# first, combine all the matched rack results (sample, levels, DOC, sample_DateTime) from each site
racksDOC <- rbind(wks_matched, L.Head_matched, Chriscrk_matched, cragg_matched, west_matched, tunnel_matched) %>%
  mutate(sample_type = "rack") %>% 
  rename(sample_DateTime = sample_time, 
         obs.filling.stage = Fill.Stage_cm,
         racksample_stage = sample_stage) %>% 
  select(-index) 

str(racksDOC)

# next, filter grabs results for DOC and combine with rack results
# grabs data (all sites) 
str(grabs_df)

grabsDOC <- grabs_df %>% 
  filter(analysis == "DOC") %>% 
  select(event = event_capture, 
         site = Site, 
         obs.filling.stage = filling.stage.cm, 
         analysis, 
         Result,
         sample_DateTime = Grab_DateTime 
  ) %>% 
  mutate(sample_type = "Grab",
         racksample_stage = "NA"
  )
# check the structures match
str(grabsDOC)
str(racksDOC)

# merge the two 
DOCresults_df <- rbind(grabsDOC, racksDOC)
str(DOCresults_df)

# add latitude and longitude so you can import this to QGIS
# check names
install_df$Sample_Name
unique(DOCresults_df$site)
site_names

# match lat and long to site names
DOCresults_df <- DOCresults_df %>% 
  mutate(
    latitude = case_when(
      DOCresults_df$site == site_names[1] ~ install_df$Latitude[1],
      DOCresults_df$site == site_names[2] ~ install_df$Latitude[2],
      DOCresults_df$site == site_names[3] ~ install_df$Latitude[3],
      DOCresults_df$site == site_names[4] ~ install_df$Latitude[4],
      DOCresults_df$site == site_names[5] ~ install_df$Latitude[5],
      DOCresults_df$site == site_names[6] ~ install_df$Latitude[6]),
    longitude = case_when(
      DOCresults_df$site == site_names[1] ~ install_df$Longitude[1],
      DOCresults_df$site == site_names[2] ~ install_df$Longitude[2],
      DOCresults_df$site == site_names[3] ~ install_df$Longitude[3],
      DOCresults_df$site == site_names[4] ~ install_df$Longitude[4],
      DOCresults_df$site == site_names[5] ~ install_df$Longitude[5],
      DOCresults_df$site == site_names[6] ~ install_df$Longitude[6])
  )

# check structure
str(DOCresults_df)

# add a column for sampling month
DOCresults_df <- DOCresults_df %>% mutate(sample_month = month(sample_DateTime, label = TRUE))
str(DOCresults_df)

# save a copy as a csv file
write.csv(DOCresults_df, file = "2019-05-26_combined-DOC-results.csv")


# --- --- --- --- #  

# summary stats
str(DOCresults_df)

DOC_stats <- DOCresults_df %>% 
  filter(analysis == "DOC") %>% 
  group_by(sample_month, site) %>% 
  summarize(count = n(), DOCmean = mean(Result), DOCsd = sd(Result), DOCmedian = median(Result), DOCmin = min(Result), DOCmax = max(Result))
head(DOC_stats)
tail(DOC_stats)
str(DOC_stats)

write.csv(DOC_stats, file = "2019-05-26_DOC-SummaryStats.csv")


# summary stats 2.0
str(DOCresults_df)

DOC_stats2 <- DOCresults_df %>% 
  filter(analysis == "DOC") %>% 
  group_by(site) %>% 
  summarize(count = n(), DOCmean = mean(Result), DOCsd = sd(Result), DOCmin = min(Result), DOCmedian = median(Result), DOCmax = max(Result))
head(DOC_stats2)
tail(DOC_stats2)
str(DOC_stats2)

write.csv(DOC_stats2, file = "2019-05-28_DOC-SummaryStats.csv")

# summary stats 3.0
str(DOCresults_df)

DOC_stats3 <- DOCresults_df %>% 
  filter(analysis == "DOC") %>% 
  group_by(site, sample_type) %>% 
  summarize(count = n(), DOCmean = mean(Result), DOCsd = sd(Result), DOCmin = min(Result), DOCmedian = median(Result), DOCmax = max(Result))
head(DOC_stats3)
tail(DOC_stats3)
str(DOC_stats3)

write.csv(DOC_stats3, file = "2019-05-28_DOC-SummaryStats3.csv")

```

```{r DOC_plots}
setwd("C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/")
# check dataframe
str(DOCresults_df)

# get factors in order for tidy calls
# set sample type to be factor
DOCresults_df$sample_type <- as.factor(DOCresults_df$sample_type)
str(DOCresults_df)

# add ordered site factor (headwater to reach)
DOCresults_df$site_f <- factor(DOCresults_df$site, levels=c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))
levels(DOCresults_df$site_f) <- site_captions2  # rename with caption names

# add ordered months (fall 2018 to spring 2019)
DOCresults_df$month_f <- factor(DOCresults_df$sample_month, levels=c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr"))

# vector to call text format for plots
textformat <- element_text(size = 14, colour = forWater_colours[4])

# make plots
# boxplot and scatter plot of DOC at all sites over first wet season
DOC_facetB.Plot <- DOCresults_df %>% filter(analysis == "DOC") %>% group_by(sample_type) %>% 
  ggplot(aes(x = month_f, y = Result, fill = sample_type, colour = sample_type)) + geom_boxplot() +
  scale_fill_manual(values = c("white", "white")) + guides(fill = FALSE) +
  geom_point(aes(colour = sample_type), size = 3) +
  scale_color_manual(values = c(forWater_colours[1], forWater_colours[5]),
                     labels = c("Grab", "Rack")) +
  theme_bw() +
  theme(legend.position = "top",
        legend.title = textformat,
        legend.text = textformat,
        axis.title = textformat,
        strip.text = element_text(size = 12, colour = forWater_colours[4]),
        axis.text = textformat) +
  labs(colour = "Sample Type:  ") +
  ylab("Dissolved Organic Carbon (mg/L NPOC)") + 
  xlab("") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~site_f) 
DOC_facetB.Plot

# scatterplot of DOC at all sites over first wet season
# scatter only (better than box plot version I think)
DOC_facet_SPlot <- DOCresults_df %>% filter(analysis == "DOC") %>% group_by(sample_type) %>% 
  ggplot(aes(x = sample_DateTime, y = Result)) +
  geom_point(aes(colour = sample_type), size = 5, alpha = 0.75) +  # partially transparent points with alpha <1
  scale_color_manual(values=c(forWater_colours[4], forWater_colours[5]),
                     labels = c("Grab", "Rack")) +
  theme_bw() +
  theme(legend.position = "top",
        legend.title = textformat,
        legend.text = textformat,
        axis.title = textformat,
        strip.text = element_text(size = 12, colour = forWater_colours[4]),
        axis.text = textformat) +
  labs(colour = "Sample Type:  ") +
  ylab("DOC (mg/L NPOC)") + 
  xlab("") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~site_f) 
DOC_facet_SPlot

ggsave(filename = "DOC_facet-scatterPlot_allSites.png", DOC_facet_SPlot)


# scatterplot of DOC at each site
# set it up and run a loop
# use vectors defined in chunk "tidy-names"

for (i in seq_along(site_names)) {
  g <- DOCresults_df %>% filter(analysis == "DOC" & site == site_names[i]) %>% group_by(sample_type) %>% 
    ggplot(aes(x = sample_DateTime, y = Result)) + 
    geom_point(aes(colour = sample_type), size = 5) +
    theme_bw() +
    theme(plot.caption = textformat,
          legend.position = c(0.8, 0.8),
          legend.text = textformat,
          legend.title = textformat,
          axis.text = textformat,
          axis.title = textformat) +
    labs(colour = "Sample Type") +
    #caption = paste("DOC over 2018-2019 wet season at ", site_captions[i])) +
    scale_color_manual(values=c(forWater_colours[4], forWater_colours[5]),
                       labels = c("Grab", "Rack")) +
    ylab("NPOC (mg/L DOC)") + 
    xlab("")
  
  ggsave(filename = paste("DOC_scatterPlot_",i,"_",site_names[i],".png"),
         width = 7.29, height = 4.5, units = "in")
}

# YAY that worked!!!! 
# Go back to your janky mess of plots above (when you have time) and fix that code up to be cool like this!!! :)

```

See if there is a direct relationship (suspected) between DOC (from grabs) and metals resutls

import both files and combine.

```{r DOC-metals}

setwd("C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/")

# read in grab sample data
grabs_df <- read.csv("2019-05-24_Grab-Sample_TOC-V_Results.csv")
str(grabs_df)

grabs_df$analysis_date <- as.POSIXct(grabs_df$analysis_date, tz = TZ)
grabs_df <- grabs_df %>% 
  mutate(collection_DateTime = as.POSIXct(paste(collection.date, collection.time), format="%Y-%m-%d %H:%M", tz = TZ))
str(grabs_df)

# read in metals + DOC data (manually merged)
metals_df <- read.csv("Leech_metals+DOC_compiled.csv", stringsAsFactors = FALSE)
str(metals_df)

# sample collection date-time as POSIXct
metals_df$Sampling.Date <- parse_date_time(metals_df$Sampling.Date, c("Ymd HM"), tz = TZ)
rename(metals_df, Sample_DateTime = Sampling.Date)
metals_df$Site <- as.factor(metals_df$Site.1)
metals_df <- subset(metals_df, select = c(-Site.1))
str(metals_df)


# replace analytical results that are below reportable detection limits with NA
# there should be a way tidier to loop over the whole data frame rather than cherry picking the character columns 
# this works, but only if the SCV format never changes
for(i in c(9, 11, 12, 14:20, 22:26, 28, 30:36, 39, 41)) {
  is.na(metals_df[,i]) <- startsWith(metals_df[,i], "<")
}

# convert from wide to long format
# The arguments to gather():
# - data: original (wide) Data object
# - key: Name of new key column (made from names of data columns)
# - value: Name of new value column
# - ...: Names of source columns that contain values
# - factor_key: Treat the new key column as a factor (instead of character vector)
metals_long <- gather(metals_df, key = "parameter", value = "result", 
                      NPOC_mg.L:Total.Sulphur..S._mg.L, na.rm=TRUE, convert=TRUE, factor_key=FALSE)
str(metals_long)

# results should be numeric not character
# convert all results values to numeric
metals_long$result <- sapply(metals_long$result, as.numeric)
str(metals_long)
head(metals_long)
tail(metals_long)

write.csv(metals_long, file = "R-outputs/2019-05-26_metals-long.csv")
write.csv(metals_df, file = "R-outputs/2019-05-26_metals-wide.csv")


```

```{r plot_metals}

setwd("C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/")

metals_nona <- read.csv("2019-05-26_metals-wide_filtered.csv")

# add ordered factor for headwater to reach
metals_nona$Site_f <- factor(metals_nona$Site, levels=c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))
levels(metals_nona$Site_f) <- site_captions

metalsnames <- as.vector(colnames(metals_nona))
metalsnames

metalsnames[8]
CaCo3 <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,8])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Total Hardness (mg/L CaCO3)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
CaCo3

metalsnames[9]
Hg <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,9])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Mercury (ug/L Hg)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Hg

metalsnames[10]
Al <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,10])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Aluminum (ug/L Al)") + 
  xlab("DOC (mg/L)") +
  geom_hline(yintercept = 100, linetype = "solid", colour = forWater_colours[5], size = 0.4) +
  facet_wrap(~Site_f) 
Al

metalsnames[12]
Ba <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,12])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Barium (ug/L Ba)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Ba

metalsnames[15]
Cu <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,15])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Copper (ug/L Cu)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Cu

metalsnames[16]
Fe <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,16])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Iron (ug/L Fe)") + 
  xlab("DOC (mg/L)") +
  geom_hline(yintercept = 300, linetype = "solid", colour = forWater_colours[5], size = 0.4) +
  facet_wrap(~Site_f) 
Fe

metalsnames[17]
Mn <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,17])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Manganese (ug/L Mn)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Mn

metalsnames[19]
Si <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,19])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Silicon (ug/L Si)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Si

metalsnames[21]
Sr <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,21])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Strontium (ug/L Sr)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Sr

metalsnames[24]
Ca <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,24])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Calcium (ug/L Ca)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Ca

metalsnames[25]
Mg <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,25])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Magnesium (ug/L Mg)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Mg

metalsnames[26]
K <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,26])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("potassium (ug/L K)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
K

metalsnames[27]
Na <- metals_nona %>% 
  ggplot(aes(x = NPOC_mg.L, y = metals_nona[,27])) + 
  geom_point(aes(colour = Trip), size = 4) +
  ylab("Sodium (ug/L Na)") + 
  xlab("DOC (mg/L)") +
  facet_wrap(~Site_f) 
Na

# save pics
ggsave("metals_CaCo3.png", CaCo3)
ggsave("metals_Hg.png", Hg)
ggsave("metals_Al.png", Al)
ggsave("metals_Ba.png", Ba)
ggsave("metals_Cu.png", Cu)
ggsave("metals_Fe.png", Fe)
ggsave("metals_Mn.png", Mn)
ggsave("metals_Si.png", Si)
ggsave("metals_Sr.png", Sr)
ggsave("metals_Ca.png", Ca)
ggsave("metals_Mg.png", Mg)
ggsave("metals_K.png", K)
ggsave("metals_Na.png", Na)

```

# 2019-05-27 
Retrying hydrograph plots with sample dots
this didn't work - keep trying
The problem was that I couldn't call the hydrograph plot I saved to a list to add it to a new ggplot() with geom_points
But I think I should be able to...


```{r chemograph_inprogress}



# plot_wks_stg, plot_L.head_stg, plot_chris_stg, plot_cragg_stg, plot_west_stg, plot_tunnel_stg

# try this

# assign rack + grab subset
rack_ss <- filter(DOCresults_df, analysis == "DOC" & sample_type == "rack")
grab_ss <- filter(DOCresults_df, analysis == "DOC" & sample_type == "Grab")

c <- plot_wks_stg +
  geom_point(data = rack_ss, aes(x = sample_DateTime, y = racksample_stage), colour = forWater_colours[4], size = 5) +
  geom_point(data = grab_ss, aes(x = sample_DateTime, y = obs.filling.stage), colour = forWater_colours[4], size = 5)
c 

## still not working

# old 
# --- INPUTS --- #
Site.Name <- site_names[1]
rackDOC <- wks_matched
stg_DOCplot <- plot_wks_stg
# grab data (site name)
grabDOC <- grabs_df %>% 
  filter(analysis == "DOC" & Site == site_names[1]) %>% 
  select(Site, sample, filling.stage.cm, Grab_DateTime, Result)
# --- get fancy --- #
c <- stg_DOCplot +
  geom_point(data = grabDOC, aes(x = Grab_DateTime, y = filling.stage.cm, size = 4), colour = forWater_colours[4], show.legend = FALSE) +
  geom_point(data = rackDOC, aes(x = sample_time, y = sample_stage, size = 4), colour = forWater_colours[5], show.legend = FALSE) 
c 
# --- --- --- --- # end old, start new

# new

# use results df
str(DOCresults_df)
# call on 'stagePlots_list' and 'site_names' to access hydrographs and names (1:6)


# --- INPUTS --- #
Site.Name <- site_names[1]
DOCdf <- DOCresults_df %>% filter(site == site_names[1] & analysis == "DOC")
hydrograph <- stagePlots_list[1]

b <- DOCresults_df %>% filter(site == site_names[1] & analysis == "DOC") %>% 
  ggplot(aes(x = sample_DateTime, y = racksample_stage)) +
  geom_point(aes(colour = sample_type), size = 4) 
b 

# stage-plot + geom_point(sample_data)

# --- diff code example
# scatterplot of DOC at each site
# set it up and run a loop
# use vectors defined in chunk "tidy-names"

for (i in seq_along(site_names)) {
  g <- DOCresults_df %>% filter(analysis == "DOC" & site == site_names[i]) %>% group_by(sample_type) %>% 
    ggplot(aes(x = sample_DateTime, y = Result)) + 
    geom_point(aes(colour = sample_type), size = 5) +
    theme_bw() +
    theme(plot.caption = textformat,
          legend.position = c(0.8, 0.8),
          legend.text = textformat,
          legend.title = textformat,
          axis.text = textformat,
          axis.title = textformat) +
    labs(colour = "Sample Type",
         caption = paste("DOC over 2018-2019 wet season at ", site_captions[i])) +
    scale_color_manual(values=c(forWater_colours[4], forWater_colours[5]),
                       labels = c("Grab", "Rack")) +
    ylab("NPOC (mg/L DOC)") + 
    xlab("")
  
  ggsave(filename = paste("DOC_scatterPlot_",i,"_",site_names[i],".png"), g)
}

# save as a picture
ggsave(paste("sample-hydrgr_", Site.Name, ".png"), plot = site.visit.plot, 
       path = "C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/R-outputs/",
       width = 7.29, height = 4.5, units = "in")

# --- fancy --- #
```




# fix up this janky code:

```{r JankyShit_fix_gtables}

## ------- you got this far in jank repair ---------##
# set up for combo plot (rainfall-streamflow)
# save each stage plot in a list to call later
stg_gtable_list <- vector("list", 6)

for (i in seq_along(stagePlots_list)) {
  stg_gtable_list[[i]] <- ggplot_gtable(ggplot_build(stagePlots_list[i]))
}

# rename the list elements of stage plot ggplot gtables
names(stg_gtable_list) <- paste(site_names,"gtable")



# ****** YOU CANT GET RID OF THIS BECAUSE THE JANKY CHEMOGRAPHS PULL ON THESE HYDROGRAPHS - UGH *** ######
# don't use this janky shit 
# BUT -- make sure you got the the ggplot gtables set up properly in your loop (to build rapid-runoff plots (but make them better, the rain bars are too thin to see))

#### -- janky shit Below --- ####
# Janky but it works

# chose the colour you want
forWater_col <- forWater_colours[3]

# --- Weeks Lake Outlet --- #
plot_wks_stg <- ggplot(filter(stage.event_dfSS5, site == site_names[1]), 
                       aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(colour = forWater_colours[4]),
        axis.text = element_text(colour = forWater_colours[4])) +
  labs(x = "", y = "Stage (cm)", caption = site_captions[1])
plot_wks_stg 

# set up for combo plot (rainfall-streamflow)
gtb_wks_stg <- ggplot_gtable(ggplot_build(plot_wks_stg))


# --- Leech River Head --- #
plot_L.head_stg <- ggplot(filter(stage.event_dfSS5, site == site_names[2]), 
                          aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(colour = forWater_colours[4]),
        axis.text = element_text(colour = forWater_colours[4])) +
  labs(x = "", y = "Stage (cm)", caption = site_captions[2])
plot_L.head_stg 

# set up for combo plot (rainfall-streamflow)
gtb_L.head_stg <- ggplot_gtable(ggplot_build(plot_L.head_stg))


# --- Chris Creek --- #
plot_chris_stg <- ggplot(filter(stage.event_dfSS5, site == site_names[3]), 
                         aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(colour = forWater_colours[4]),
        axis.text = element_text(colour = forWater_colours[4])) +
  labs(x = "", y = "Stage (cm)", caption = site_captions[3])
plot_chris_stg 

# set up for combo plot (rainfall-streamflow)
gtb_chris_stg <- ggplot_gtable(ggplot_build(plot_chris_stg))

## note data gap 2018-11-07 -- date of re-build. 
# Original installation by Bill Floyd was at an angle, Nov 7 Stew and Hannah re-built the station to be vertical and match other designs. 
# In the original structure, the sensor was laying against the inside of the stilling well (possibly resulting in a positive bias)
# the angled stilling well may have extended the offset (if the stilling well wasn't against the streambed). 
# all bottle heights for the pre and post period are matched to the stilling well, so they should still line up.


# --- Cragg Creek --- #
plot_cragg_stg <- ggplot(filter(stage.event_dfSS5, site == site_names[4]), 
                         aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(colour = forWater_colours[4]),
        axis.text = element_text(colour = forWater_colours[4])) +
  labs(x = "", y = "Stage (cm)", caption = site_captions[4])
plot_cragg_stg 

# set up for combo plot (rainfall-streamflow)
gtb_cragg_stg <- ggplot_gtable(ggplot_build(plot_cragg_stg))


# --- West Leech River (above the confluence with Leech mainstem) --- #
plot_west_stg <- ggplot(filter(stage.event_dfSS5, site == site_names[5]), 
                        aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(colour = forWater_colours[4]),
        axis.text = element_text(colour = forWater_colours[4])) +
  labs(x = "", y = "Stage (cm)", caption = site_captions[5])
plot_west_stg 

# set up for combo plot (rainfall-streamflow)
gtb_west_stg <- ggplot_gtable(ggplot_build(plot_west_stg))



# --- Tunnel --- #
plot_tunnel_stg <- ggplot(filter(stage.event_dfSS6, site == site_names[6]), 
                          aes(x = DateTime, y = Stage_cm)) + 
  geom_point(col = forWater_col) + 
  theme_minimal() + 
  theme(#axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    text = element_text(colour = forWater_colours[4]),
    axis.text = element_text(colour = forWater_colours[4])) +
  labs(x = "", y = "Stage (cm)", caption = site_captions[6])
plot_tunnel_stg 

# set up for combo plot (rainfall-streamflow)
gtb_tunnel_stg <- ggplot_gtable(ggplot_build(plot_tunnel_stg))


```

Create rainfall runoff plots

```{r rainfall-runoff_plots_janky}

setwd("C:/Users/Hannah/Documents/UBC_MSc/Analyses+Laboratory+Tracking_forWater-MSc_HMc/Data_WORKUP_forWater-MSc_HMc/")

# create rainfall and stream level plots and save each as an image

# Site 1 ------------------------------- 
# Weeks Lake Outlet 
# with CC-Wx 
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], 
                      gtb_wks_stg$widths[2:3])
gpt_wx_CC$widths[2:3] <- maxWidth
gtb_wks_stg$widths[2:3] <- maxWidth

rr_WksOut_CC <- grid.arrange(gpt_wx_CC, gtb_wks_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_WksOut-CC.png", rr_WksOut_CC)


# Site 2  ------------------------------- 
# Leech River Head (below colfluence of Chris and Weeks) 
# with CC-Wx
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], 
                      gtb_L.head_stg$widths[2:3])
gpt_wx_CC$widths[2:3] <- maxWidth
gtb_L.head_stg$widths[2:3] <- maxWidth

rr_LHead_CC <- grid.arrange(gpt_wx_CC, gtb_L.head_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_LHead-CC.png", rr_LHead_CC)


# Site 3  ------------------------------- 
# Chris Creek
# with CC-Wx 
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], gtb_chris_stg$widths[2:3])
gpt_wx_CC$widths[2:3]  <- maxWidth
gtb_chris_stg$widths[2:3] <- maxWidth

rr_chris_CC <- grid.arrange(gpt_wx_CC, gtb_chris_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_chris-CC.png", rr_chris_CC)


# Site 4   ------------------------------- 
# Cragg Creek 
# with CC-Wx 
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], 
                      gtb_cragg_stg$widths[2:3])
gpt_wx_CC$widths[2:3] <- maxWidth
gtb_cragg_stg$widths[2:3] <- maxWidth

rr_cragg_CC <- grid.arrange(gpt_wx_CC, gtb_cragg_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_cragg-CC.png", rr_cragg_CC)


# Cragg Creek
# with MG-Wx 
maxWidth <- unit.pmax(gpt_wx_MG$widths[2:3], 
                      gtb_cragg_stg$widths[2:3])
gpt_wx_MG$widths[2:3] <- maxWidth
gtb_cragg_stg$widths[2:3] <- maxWidth

rr_cragg_MG <- grid.arrange(gpt_wx_MG, gtb_cragg_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_cragg-MG.png", rr_cragg_MG)


# Site 5  ------------------------------- 
# West Leech River 
# with MG-Wx
maxWidth <- unit.pmax(gpt_wx_MG$widths[2:3], 
                      gtb_west_stg$widths[2:3])
gpt_wx_MG$widths[2:3] <- maxWidth
gtb_west_stg$widths[2:3] <- maxWidth

rr_WLeech_MG <- grid.arrange(gpt_wx_MG, gtb_west_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_WLeech-MG.png", rr_WLeech_MG)


# West Leech River
# with CC-Wx
maxWidth <- unit.pmax(gpt_wx_CC$widths[2:3], 
                      gtb_west_stg$widths[2:3])
gpt_wx_CC$widths[2:3] <- maxWidth
gtb_west_stg$widths[2:3] <- maxWidth

rr_WLeech_CC <- grid.arrange(gpt_wx_CC, gtb_west_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_WLeech-CC.png", rr_WLeech_CC)


# Site 6  ------------------------------- This one isn't lined up properly b/c late installation 
# Leech River Tunnel 
# with CC-Wx
maxWidth <- unit.pmax(gpt_wx_CC_tunnelspan$widths[2:3], 
                      gtb_tunnel_stg$widths[2:3])
gpt_wx_CC_tunnelspan$widths[2:3] <- maxWidth
gtb_tunnel_stg$widths[2:3] <- maxWidth

rr_Tunnel_CC <- grid.arrange(gpt_wx_CC_tunnelspan, gtb_tunnel_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_Tunnel-CC.png", rr_Tunnel_CC)

# Leech River Tunnel 
# with MG-wx
maxWidth <- unit.pmax(gpt_wx_CC_tunnelspan$widths[2:3], 
                      gtb_tunnel_stg$widths[2:3])
gpt_wx_MG_tunnelspan$widths[2:3] <- maxWidth
gtb_tunnel_stg$widths[2:3] <- maxWidth

rr_Tunnel_MG <- grid.arrange(gpt_wx_MG_tunnelspan, gtb_tunnel_stg, ncol = 1, heights = c(1, 3))
ggsave("R-outputs/rr-plot_Tunnel-MG.png", rr_Tunnel_MG)

```




