---
title: "Reproducible data analysis: thesis data visualization and analysis"
subtitle: "Pacific Maritime forWater Masters Project (NSERC forWater)"
author: "Hannah J McSorley"
output: bookdown::word_document2
---

# Data Visualization and Summaries

## Set-up

```{r, processing-setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, fig.path="R-outputs_UBC-forWater-MSc_HMc/figures/")
# save figures to folder 'figures' in the 'R-outputs...' folder
```

```{r, processing-packages, package.startup.message = FALSE, include=FALSE}

# load packages
library(tidyverse)  # includes: dplyr, ggplot2, purrr, readr, forcats, lubridate
library(knitr)      # tidy tables
library(viridis)    # nice colours for plots gradient fills
library(ggpmisc)    # linear regression line values
library(cowplot)    # add-on to ggplot for layout
library(gghighlight)# plot highlighting

```

```{r vectorize-colours}
# use forWater defined colours (hexadecimal codes) for plots
# all colours defined by forWater admin, except 'MyOrange' which I made
forWater_colours <- c(MainBlue = "#09A4D2", 
                      MainGreen = "#668536", 
                      AccentBlue = "#5B99CC", 
                      DarkGrey = "#3B3838", 
                      MyOrange = "#f4AB0E")

# colour-blind friendly pallet with grey (no black)
cbPalette <- c(grey = "#999999", 
               orange = "#E69F00", 
               lightblue = "#56B4E9", 
               green = "#009E73", 
               yellow = "#F0E442", 
               darkblue = "#0072B2", 
               red = "#D55E00", 
               pink = "#CC79A7")
```

## load datasets
```{r, input-files, message=FALSE}
# assign timezone
TZ <- "Etc/GMT+8"

# File Inputs
#Results of data wrangling (01) were saved as .csv files for tidy loading. 
# read all compiled data files & format

# sampleresults df
# compiled sample analyses results (wide)

sampleresults <- read_csv("R-outputs_UBC-forWater-MSc_HMc/samples-lab-analyses_results.csv",
                          col_names = TRUE) %>%   
  mutate(trip = factor(trip, levels = c(1:22)),
         sample_type = factor(sample_type),
         sample = factor(sample),
         analysis = factor(analysis),
         three_seasons = factor(three_seasons),
         two_seasons = factor(two_seasons),
         pseudoSUVA = pseudo254/NPOC_ppm) %>% 
  mutate(site = factor(site),
         # remove dashes from sub-basin names (match Odyssey names)
         site = forcats::fct_recode(site, 
                                    Weeks = "Weeks-out",
                                    ChrisCrk = "Chris-crk",
                                    LeechHead = "Leech-head",
                                    CraggCrk = "Cragg-crk", 
                                    WestLeech = "West-Leech")) 

# odyssey_data df
# stage data compiled with interval/trip
odyssey_data <- read_csv("R-outputs_UBC-forWater-MSc_HMc/Odyssey-RackCorrected-stage.csv",
                         col_names = TRUE) %>% 
   mutate(source = factor(source,
                          levels = c("Weeks", "ChrisCrk", "LeechHead", "CraggCrk", "WestLeech", "Tunnel")),
         interval = factor(interval),
         DateTime = lubridate::ymd_hms(DateTime, tz = TZ))

# precip_data df
# 2018-2020 weather station data compiled and formatted
precip_data <- read_csv("R-outputs_UBC-forWater-MSc_HMc/FWx-PrecipTemp_compiled.csv", 
                        col_names = TRUE,
                        col_types = list("c", "c", "d", "d", "d", "d", "d", "d", "d", "d", "d", "d")) %>% 
  mutate(StationName = factor(StationName),
         DateTime = lubridate::ymd_hms(DateTime, tz = TZ))    

# LWSA mean precip data (FWx-mean-LWSA df)
# 2018-2020 weather station data compiled and formatted
LWSA_meanWx <- read_csv("R-outputs_UBC-forWater-MSc_HMc/FWx-Mean-LWSA_PrecipTemp.csv", 
                        col_names = TRUE,
                        col_types = list("T", "d", "d", "d", "d", "d", "d", "d", "d", "d", "d")) %>% 
  mutate(DateTime = lubridate::ymd_hms(DateTime, tz = TZ))    


# metalslab df
# metals sample analyses results with OC (long)
metalslab <- read_csv("R-outputs_UBC-forWater-MSc_HMc/metals-DOCgrab-sample_results-long.csv",
                      col_names = TRUE) %>% 
  mutate(Trip = factor(Trip),
         site = factor(site), 
         sample_type = factor(sample_type),
         sample = factor(sample),
         analysis = factor(analysis),
         three_seasons = factor(three_seasons),
         two_seasons = factor(two_seasons),
         metal_parameters = factor(Parameters))
  
```

## Subset, sample counts
```{r, subsetting-campaign}
# primary synoptic sampling sites (n > 1)
# 15 sites total

# how many synoptic samples were grabbed?
# save value as object to implant in text
n_SynopticGrabs <- sampleresults %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab") %>%
  group_by(site = forcats::fct_explicit_na(site)) %>% 
  summarise(grab_sample_count = n()) %>% 
  filter(grab_sample_count > 1) %>% 
  mutate(what = "synoptic grab count") %>% 
  ungroup() %>%  # drop the following code to see samples by sites
  group_by(what) %>% 
  summarise(total = sum(grab_sample_count)) %>% 
  pull(total)

# -------------------
# synoptically sampled sites
# synsites <- c("WestLeech","Tunnel","CraggCrk","LeechHead","Weeks","ChrisCrk","Jarvis","Lazar","Rithet","Deception-res","West-Jordan","Leech-downstreamconf","Judge-crk","Deception-crk","Boneyard")

# create a subset dataframe for the synoptically sampled sites for tidier calling
synopticfilter <- sampleresults %>% filter(site == "Weeks"|
                                             site == "ChrisCrk"|
                                             site == "LeechHead"|
                                             site == "CraggCrk"|
                                             site == "WestLeech"|
                                             site == "Tunnel"|
                                             
                                             site == "Rithet"|
                                             site == "Lazar"|
                                             site == "Jarvis"|
                                             site == "Judge-crk"|
                                             site == "Leech-downstreamconf"|
                                             site == "Boneyard"|
                                             site == "Deception-crk"|
                                             site == "West-Jordan"|
                                             site == "Deception-res"
                                             ) %>% 
  mutate(site = factor(site, # order as you want to see them in plots
                       levels = c("Weeks", "ChrisCrk", "LeechHead", "CraggCrk", "WestLeech", "Tunnel","Leech-downstreamconf", "Boneyard", "Deception-crk", "Judge-crk", "Rithet", "Lazar", "Jarvis", "West-Jordan","Deception-res")))

# create a subset dataframe for the six install sites for tidier calling
sixfilter <- sampleresults %>% filter(site == "Weeks" |
                                        site == "LeechHead" |
                                        site == "ChrisCrk" |
                                        site == "CraggCrk" |
                                        site == "WestLeech"| 
                                        site == "Tunnel") %>% 
  mutate(site = factor(site, levels = 
                         c("Weeks", "ChrisCrk", "LeechHead", "CraggCrk", "WestLeech","Tunnel")))
# -------------------
```

#### Table: sample summary
```{r, summary table}
# how many of each sample_type are there at the 6 main sites?
n_subbbasinSamples <- sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab") %>%
  group_by(site, sample_type) %>%   
  summarise(number_of_samples = n()) %>% 
  ungroup()
# save to outputs
write_csv(n_subbbasinSamples, 
          path = "R-outputs_UBC-forWater-MSc_HMc/tables/summary_subbasins-SampleCount.csv", na = "NA") 

# how many of each type total?
# save values as objects to implant in text

# Grab samples
n_installGrabSamples <- n_subbbasinSamples %>% 
  filter(sample_type == "Grab") %>%  
  summarize(total = sum(number_of_samples)) %>% 
  pull(total)

# Rack samples
n_installRackSamples <- n_subbbasinSamples %>% 
  filter(sample_type == "Rack") %>%  
  summarize(total = sum(number_of_samples)) %>% 
  pull(total) 

# How many samples were collected overall
# 400 total
n_totalSamples <- sampleresults %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab") %>%
  #group_by(sample_type) %>% 
  summarise(sample_count = n()) %>% 
  ungroup() %>% 
  pull(sample_count)



# 15 synoptic sites (including the install sites)
synopticfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab") %>%
  group_by(site = forcats::fct_explicit_na(site)) %>% 
  summarise(grab_sample_count = n()) %>% 
  ungroup() 


# ----------------------------------
# make a summary table:
tibble::tibble(
  "synoptic samples outside of subbasin sites" = n_SynopticGrabs-n_installGrabSamples,
  "opportunistic grab samples" = n_totalSamples-(n_SynopticGrabs+n_installRackSamples),
  "sub-basin synoptic grab samples" = n_installGrabSamples,
  "sub-basin rack samples" = n_installRackSamples,
  "total" = n_totalSamples) %>% 
  pivot_longer(everything(),
               names_to = "sample category", values_to = "count") %>% 
  write_csv("R-outputs_UBC-forWater-MSc_HMc/tables/summary_AllSamples_Count.csv")

```

## Leech DOC concentrations

Table 1 and Figure 1 show DOC concentrations were highest at Weeks Creek, the headwaters monitoring point for a sub-basin which included Weeks Lake and surrounding wetlands. On average, Chris Creek DOC concentration was 51% lower than Weeks creek. Below the confluence of Weeks and Chris Creek, the head of Leech River had a mean DOC concentration slightly less than the average of the two headwater tributaries. West Leech River had higher DOC than Cragg Creek by about 20%. Below the confluences of West Leech and Cragg Creek, the Leech Tunnel site had DOC concentrations that were 54% lower than the average at the Leech head, and closer to those of Cragg Creek.

### Plot DOC concs across the watershed
```{r, DOCspace}

# Boxplot with jitter scatter 
# DOC by site 
# grab and rack combined (all)
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab" | sample_type == "Rack") %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none") +
  labs(caption = 
         glue::glue("DOC concentrations across six sub-basin sites over 16 months (", {n_installGrabSamples+n_installRackSamples}, " samples)"), 
       x = "", y = "DOC (mg/L)")
# save
ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/figures/", filename = "DOC_subbasin_boxplots.png")

# DOC summary table, Grabs and Racks combined
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab" | sample_type == "Rack") %>% 
  group_by(site) %>% 
  summarize(DOC_mean = mean(NPOC_ppm, na.rm = T),
            DOC_sd = sd(NPOC_ppm, na.rm = T),
            RSD = (DOC_sd/DOC_mean)*100) %>% 
  ungroup() %>% 
  write_csv("R-outputs_UBC-forWater-MSc_HMc/tables/DOC-subbasin_summary-table.csv", col_names = TRUE)

# DOC summary table -- Grab vs Rack
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab" | sample_type == "Rack") %>% 
  group_by(site, sample_type) %>% 
  summarize(DOC_mean = mean(NPOC_ppm, na.rm = T),
            DOC_sd = sd(NPOC_ppm, na.rm = T),
            RSD = (DOC_sd/DOC_mean)*100) %>% 
  ungroup() %>% 
  write_csv("R-outputs_UBC-forWater-MSc_HMc/tables/DOC-subbasin_RvsG_summary-table.csv", col_names = TRUE)
  
```

### WIP- Rack DOC (by level)
```{r, rackDOC}

sixfilter %>% 
  filter(sample_type == "Rack") %>% 
  mutate(trip = factor(trip, levels = c(1:23))) %>% 
  group_by(site, trip) %>% 
  mutate(RisingLimb = NumberXtract(sample),
         RisingLimb = factor(RisingLimb, levels = c(1:15))) %>% 
  ggplot(aes(x = NPOC_ppm, y = RisingLimb)) +
  geom_jitter(aes(colour = site)) +
  facet_wrap(~trip)
  
```

### DOC conc table (synoptic)
```{r, Grab-synoptic-table}

# synoptic grab samples DOC concs
# by site
synopticfilter %>%
  mutate(site = forcats::fct_recode(site, 
                                    LeechBeach = "Leech-downstreamconf",
                                    DeceptionGulch = "Deception-crk",
                                    JudgeCrk = "Judge-crk",
                                    WestJordan = "West-Jordan",
                                    DeceptionReservoir = "Deception-res")) %>% # new name = "old name"
  filter(sample_type == "Grab") %>% 
  group_by(site) %>% 
  summarize(count = n(), 
            DOCmean = mean(NPOC_ppm, na.rm = T), 
            DOCsd = sd(NPOC_ppm, na.rm = T), 
            DOCmin = min(NPOC_ppm, na.rm = T), 
            DOCmedian = median(NPOC_ppm, na.rm = T), 
            DOCmax = max(NPOC_ppm, na.rm = T)) %>% 
  write_csv(path = "R-outputs_UBC-forWater-MSc_HMc/tables/DOC-GrabSynoptic_site-conc-summary.csv", col_names = T)

# all together
synopticfilter %>%
  filter(sample_type == "Grab") %>% 
  summarize(count = n(), 
            DOCmean = mean(NPOC_ppm, na.rm = T), 
            DOCsd = sd(NPOC_ppm, na.rm = T), 
            DOCmin = min(NPOC_ppm, na.rm = T), 
            DOCmedian = median(NPOC_ppm, na.rm = T), 
            DOCmax = max(NPOC_ppm, na.rm = T)) %>% 
  write_csv(path = "R-outputs_UBC-forWater-MSc_HMc/tables/DOC-GrabSynoptic_all-conc-summary.csv", col_names = T)

# all together including rack samples
synopticfilter %>%
  filter(sample_type == "Grab" | sample_type == "Rack") %>% 
  summarize(count = n(), 
            DOCmean = mean(NPOC_ppm, na.rm = T), 
            DOCsd = sd(NPOC_ppm, na.rm = T), 
            DOCmin = min(NPOC_ppm, na.rm = T), 
            DOCmedian = median(NPOC_ppm, na.rm = T), 
            DOCmax = max(NPOC_ppm, na.rm = T)) %>% 
  write_csv(path = "R-outputs_UBC-forWater-MSc_HMc/tables/DOC-Synoptic_all-conc-summary.csv", col_names = T)

```

## Subbasins 

At the six sub-basin monitoring sites, vertical racks were installed to collect samples as the rivers rose in response to precipitation events.

These vertical racks collected samples on the rising hydrograph limb, which has been shown to have higher DOC concentration that non-storm flow [@Yang2015; @Raymond2016; @Raymond2010]. As the vertical racks require a hydrologic response to collect samples, they are only applicable during the wet season. Comparing wet season Grab samples to those collected on Racks confirms that the rack samplers were able to capture more samples, and many during periods with higher DOC concentrations (Fig.2).  

##### DOC boxplot (G/R)

```{r, DOC-space-time-boxplot}
# Boxplot with jitter scatter 
# site vs DOC
# facet wrap by sample type
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab",
                two_seasons == "wet") %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~sample_type, ncol = 2, nrow = 1) +  
  labs(caption = (glue::glue("DOC concentration by sample type and site during wet season \n
       Grab samples (n =  {n_installGrabSamples} ) and rising limb Rack samples (n =  {n_installRackSamples})")), 
       x = "", y = "DOC (mg/L)")
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/DOC-subbasin_GvsR_boxplot.png") 


```

##### DOC ridgeplot (G/R)

```{r, sample_type-ridgeplots, include=FALSE, echo = FALSE}

# density ridge 
# wrap by sample_type
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab" & sample == "Grab") %>%
  ggplot(aes(x = NPOC_ppm, y = fct_rev(site))) +
  ggridges::geom_density_ridges(aes(fill = site), alpha = 0.4) +
  facet_wrap(~sample_type, ncol = 1, nrow = 2) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  labs(y = "", x = "DOC (mg/L)", 
       caption = glue::glue("Density distribution plots of DOC concentration by sample type and site \n
       Grab samples (n =  {n_installGrabSamples} ) and rising limb Rack samples (n =  {n_installRackSamples})")) +
  theme(legend.position = "none") 

ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/DOC_subbasin-ridgeplot_GvsR.png")


```

##  Sampling campaign
Four hundred water sample were collected and analyzed for DOC over a 16 month study period (October 2018 to February 2020). The synoptic grab-sampling program was enhanced by the collection of stormflow on the six vertical sampling racks. In total, 171 samples were collected on vertical Racks, 215 Grab samples were collected at 15 synoptically sampled sites (which included the six installation sites), and an additional 14 Grab samples were collected opportunistically at one-off sites across the water supply area. Figure 3 shows DOC concentrations across the 15 synoptically sampled sites over the study period (n=386). 

```{r DOC-buckshot-plot_sample_type}

# DOC over time by sample_type
synopticfilter %>% 
  dplyr::filter(analysis == "DOC",
                sample_type == "Grab" | sample_type == "Rack") %>%
  mutate(trip_end = factor(trip_end)) %>% 
  ggplot(aes(x = trip_end, y = NPOC_ppm)) + 
  geom_jitter(aes(fill = sample_type), size = 3, shape = 22, alpha = 0.75) +
  scale_fill_manual(values = c("#D55E00", "#999999")) +
  theme_bw() +
  labs(y = "DOC (mg/L)", x = "", fill = "sample type",
       caption = "Fig.3 DOC over fifteen months (Oct 2018 to Jan 2020) in 386 samples \n(synoptic Grab samples (n = 215) and vertical Rack collection (n = 171)") +
  theme(axis.text.x = element_text(angle = 90), legend.position = "top")

ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/buckshot_DOC-total-sampletype.png") 
```
Over the study period, DOC concentrations decreased throughout the wet season, and increased again during the dry summer months (Fig.3). This seasonal DOC concentration pattern was clear at each of the six installation locations in the LWSA (Fig.4).

```{r DOC over time at 6 sites by sample_type, fig.width=8, fig.height=6, echo = FALSE}
# at each of the six sites (DOC over time)
sixfilter %>% 
  dplyr::filter(analysis == "DOC",
                sample_type == "Rack" | sample_type == "Grab") %>%
  mutate(trip = factor(trip)) %>% 
  ggplot(aes(x = trip, y = NPOC_ppm)) +
  geom_jitter(aes(fill = sample_type), size = 2, shape = 21, alpha = 0.6) +
  scale_fill_manual(values = c("#D55E00", "#999999")) +
  theme_bw() +
  labs(y = "DOC (mg/L)", x = "field trip", fill = "sample type:",
       caption = "Fig.4 DOC over fifteen months (Oct 2018 to Jan 2020) in 324 samples \n(Grab samples (n = 153) and vertical Rack collection (n = 171)") +
  facet_wrap(~site, ncol = 2, nrow = 3) +
  theme(axis.text.x = element_text(angle = 90), legend.position = "top")

ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/buckshot_DOC-subbasins-sampletype.png") 

```


### DOC and metals in solution

Aquatic NOM can play an important role in the transport of metals because it has the physiochemical ability to act as a ligand to create coordinated complexes with metals. From November 2018 to July 2019, I collected eight sets of samples for metals analysis from the six sub-basin monitoring sites. Metals samples were collected on behalf of the CRD and were analyzed at Bureau Veritas Laboratories in Sidney, BC (formerly Maxxam Analytics Inc.). For each metals sample collected, a parallel Grab sample was analyzed for DOC. There was a suite of metals included in the analyses, many of which were below detection limits; Figure XXXXX shows DOC concentrations from samples which had detectable concentrations of eight metal species.   


```{r, metals-NPOC, echo = FALSE}
# filter out the parameters with insufficient data
# plot DOC against metals concentrations 
metalslab %>% filter(metal_parameters == "Total Aluminum (Al)"|
                       metal_parameters == "Total Barium (Ba)"|
                       metal_parameters == "Total Copper (Cu)"|
                       metal_parameters == "Total Iron (Fe)"|
                       metal_parameters == "Total Mercury (Hg)"|
                       metal_parameters == "Total Manganese (Mn)"
                       #metal_parameters == "Total Magnesium (Mg)"|
                       #metal_parameters == "Total Silicon (Si)"
                       ) %>%
   mutate(metal_parameters = factor(metal_parameters, # order as you want to see them in plots
                       levels = c("Total Mercury (Hg)",
                                  "Total Aluminum (Al)",
                                  "Total Iron (Fe)",
                                  "Total Copper (Cu)",
                                  "Total Barium (Ba)",
                                  "Total Manganese (Mn)"
                                  #"Total Silicon (Si)",
                                  #"Total Magnesium (Mg)"
                                  ))) %>% 
  ggplot(aes(x = NPOC_ppm, 
             y = metals_values)) +
  geom_jitter(aes(shape = site)) +
  facet_wrap(~metal_parameters,
             scales = "free",
             ncol = 2) +
  theme_bw() +
  theme(legend.position ="right") +
  labs(y = "ug/L", x = "DOC (mg/L)") +
  stat_smooth(method=lm, formula = y ~ x) +
## to get equations include these lines:
  stat_poly_eq(formula = y ~ x, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE, rr.digits = 4) #+
## to check  
 #geom_hline(aes(yintercept = MAC), na.rm = TRUE)

# save
ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/figures/", filename = "DOC-Metals_subbasin_scatterplots.png")

# make a summary table of Metals regression
tibble::tibble(Metal = c("Total Mercury (Hg)", "Total Aluminum (Al)", "Total Iron (Fe)", "Total Copper (Cu)", "Total Barium (Ba)", "Total Manganese (Mn)"),
               Eqn = c("0.000437x -0.000123", "20.1x -1.21", "30.9x -74.5",
                       "0.0558x +0.403", "0.225x +2.28", "4.38x -21.4"),
               n = c("3", "37", "40", "34", 
                     "35", "15"),
               R2 = c("0.999", "0.397", "0.693", "0.176", "0.225", "0.594"))
```

DOC concentration had a strong positive relationship with total mercury (R^2^=0.9998, n=3) aluminum (R^2^=0.81, n=36), and iron (R^2^=0.72, n=36). While the relationships were not as strong, DOC was also positively related to concentrations of copper (R^2^=0.47, n=27), barium (R^2^=0.25, n=30), and manganese (R^2^=0.21, n=12). Not included in FIGUREYYYYYY is the weak inverse relationship between DOC and silicon (R^2^=0.061, n=29) and magnesium (R^2^=0.015, n=30). All metals concentrations were below maximum allowable concentrations and aesthetic objectives for source water guidelines [@BC999999999999REF].  

```{r, metals-CDOM-dontinclude}

# limited metals with DOC_eq
# filter out the parameters with insufficient data
# plot DOC agains metals concentrations
metalslab %>% filter(metal_parameters == "Total Aluminum (Al)"|
                       metal_parameters == "Total Barium (Ba)"|
                       metal_parameters == "Total Copper (Cu)"|
                       metal_parameters == "Total Iron (Fe)"|
                       #metal_parameters == "Total Mercury (Hg)"| # insufficient
                       metal_parameters == "Total Magnesium (Mg)"|
                       metal_parameters == "Total Manganese (Mn)"
                       #metal_parameters == "Total Silicon (Si)"
                       ) %>% 
  ggplot(aes(x = DOCeq_ppm, 
             y = metals_values)) +
  geom_jitter(aes(shape = site)) +
  facet_wrap(~metal_parameters,
             scales = "free",
             ncol = 2) +
  stat_smooth(method=lm) +
  theme_bw() +
  theme(legend.position ="right") +
  labs(y = "ug/L", x = "CDOM (mg/L eq.)")

```



## Seasonal examination of DOC & DOM dynamics 

In this section, a categorical season ID was used to assess temporal variations in DOC. Seasons were separated based on months of the year: the wet season was October through May, and the dry season was June until October.

* Precipitation data will be employed to operationally separate season (data obtained January 31, 2020 from CRD).

These seasonal plots show data from both Rack and Grab samples in order to include the full available range of concentrations. 

In the wet season, DOC concentrations generally increased during stormflow (relative to between-storm peaks) _{data not shown yet}_, and progressively dropped over the course of the wet season. During dry season baseflow, DOC concentration was elevated compared to late wet season DOC (Fig.5).

```{r, seasonal-DOC-table-ridgeplot, fig.width=8, fig.height=6, echo = FALSE}

# density ridge plots (facet wrap by season)
sixfilter %>% 
  dplyr::filter(analysis == "DOC",
                sample_type == "Rack" | sample_type == "Grab") %>%
  ggplot(aes(x = NPOC_ppm, y = fct_rev(site))) +
  ggridges::geom_density_ridges(aes(fill = site), alpha = 0.4) +
  facet_wrap(~two_seasons, ncol = 1, nrow = 2) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  labs(y = "", x = "DOC (mg/L)", 
       caption = "Density distribution of DOC concentration by season (dry: n = 45, wet: n = 240)") +
  theme(legend.position = "none") 
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "Fig5_DOC_ridgeplot-seasonal.png") 
```

At each of the six sub-basin monitoring locations, mean DOC was higher during the dry season than during the wet season (Table 2, Fig.8). There was less variation in dry season DOC concentrations at each site also (Table 2), which could be due to actual reduction in variance in the absence of stormflow pulses and also due to fewer dry season samples (n = 46) compared to wet season samples (n = 278). 

```{r, seasonal-DOC-table2, echo = FALSE}
# summary table
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab" | sample_type == "Rack") %>% 
  group_by(site, two_seasons) %>% 
  summarize(DOC_mean = mean(NPOC_ppm),
            DOC_sd = sd(NPOC_ppm),
            RSD = (DOC_sd/DOC_mean)*100) %>% 
  ungroup() %>% 
  knitr::kable(digits = 1, col.names = c("season", "site", "mean DOC (mg/L)", "std.dev. (± mg/L)", "RSD (%)"), label = "Table 2: DOC concentrations by season at the six main sites")

# Boxplot with jitter scatter (DOC by season)
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Rack" | sample_type == "Grab") %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~two_seasons, ncol = 2, nrow = 1) +  
  labs(caption = "Fig.8 DOC concentration by season (dry: n = 46, wet: n = 278)", 
       x = "", y = "DOC (mg/L)")

```

To remove the variance of stormflow DOC concentrations, Table 2-B and Figure 9 shows seasonal concentrations based only on Grab samples (excludes 166 stormflow samples collected by Racks).

```{r, seasonal-Grab-DOC-table2B, echo = FALSE}
# summary table (grabs only)
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab") %>% 
  group_by(site, two_seasons) %>% 
  summarize(DOC_mean = mean(NPOC_ppm),
            DOC_sd = sd(NPOC_ppm),
            RSD = (DOC_sd/DOC_mean)*100) %>% 
  ungroup() %>% 
  knitr::kable(digits = 1, col.names = c("season", "site", "mean DOC (mg/L)", "std.dev. (± mg/L)", "RSD (%)"),
               label = "Table 2-B: Grab sample DOC concentrations by season at the six main sites")

# Boxplot with jitter scatter (DOC by season)
sixfilter %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab") %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~two_seasons, ncol = 2, nrow = 1) +  
  labs(caption = "Fig.9 DOC concentration by season (dry: n = 45, wet: n = 112)", 
       x = "", y = "DOC (mg/L)")
# ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "DOC_boxplot-seasonal.png") 


```

## Spectral Indices

```{r, spectral-plots, echo = FALSE}
# SUVA vs NPOC by season
sampleresults %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab" | sample_type == "Rack") %>% 
  ggplot(aes(x = NPOC_ppm, y = SUVA)) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~two_seasons, ncol = 2, nrow = 1) 

# E2:E3
sampleresults %>% 
  dplyr::filter(analysis == "DOC", 
                sample_type == "Grab" | sample_type == "Rack",
                E2E3 < 15) %>% 
  ggplot(aes(x = NPOC_ppm, y = E2E3 )) +
  geom_jitter(aes(fill = two_seasons), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none") 
#+
 #facet_wrap(~two_seasons, ncol = 2) 
```


```{r, seasonal-plots, include=FALSE}
# Boxplot with jitter scatter 
sampleresults %>% 
  dplyr::filter(site == "Weeks" |
                  site == "LeechHead" |
                  site == "ChrisCrk" |
                  site == "CraggCrk" |
                  site == "WestLeech"| 
                  site == "Tunnel" |
                  site == "Rithet" |
                  site == "Judge-crk", 
                analysis == "DOC", 
                sample_type == "Grab" & sample == "Grab") %>% 
  mutate(site = factor(site, 
                       levels = c("Weeks", "ChrisCrk", "LeechHead", "CraggCrk", "WestLeech", "Tunnel", "Rithet", "Judge-crk"))) %>% 
  ggplot(aes(x = site, y = NPOC_ppm, fill = site)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~two_seasons, ncol = 2, nrow = 1) +  
  labs(caption = "DOC concentrations in the Leech and two main tribs to the Sooke Reservoir", 
       x = "", y = "DOC (mg/L)")


# --- DOC facet wrap scatter plots ---
# I don't think these are good graphics
# Scatter main sites including sooke tribs
sampleresults %>% 
  dplyr::filter(site == "Weeks-out" |
                  site == "Leech-head" |
                  site == "Chris-crk" |
                  site == "Cragg-crk" |
                  site == "West-Leech"| 
                  site == "Tunnel" |
                  site == "Rithet" |
                  site == "Judge-crk", 
                analysis == "DOC", 
                sample_type == "Grab" & sample == "Grab") %>% 
  mutate(site = factor(site, 
                       levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel", "Rithet", "Judge-crk"))) %>% 
  ggplot(aes(x = dt_sampled, y = NPOC_ppm, fill = sample_type)) +
  geom_jitter(aes(fill = site), alpha = 0.8, shape = 21, size = 3) +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(caption = "DOC concentrations", x = "", y = "DOC (mg/L, as NPOC)") +
  theme(axis.text.x = element_text(angle = 90), legend.position = "none") +
  facet_wrap(~site, ncol = 2, nrow = 4)
# this is not a useful plot

```


### Plots of DOC & proxy

DOC was quantified as non-purgeable organic carbon (NPOC) on the Shimadzu TOC auto analyzer, and samples were also measured on a Spectrolyser spectrophotometer. A spectrophotometer can only measure the fraction of organic matter that is able to absorb UV or Visible light, and therefore DOC measured on the Spectrolyser was a measure of CDOM and an indicator of aromaticity (molecular character).

Figure 6 shows results from all samples comparing DOC concentrations (as NPOC, direct measure) to CDOM concentrations (UV-Vis, proxy measure of DOC). There was a strong seasonal separation of the relationship between these two measurements. These results indicate a seasonally-driven physiochemical difference in the aquatic NOM in this drinking water supply area.

```{r, DOC-vs-CDOM, echo = FALSE}

# all sites: DOC vs CDOM
synopticfilter %>% 
  filter(analysis == "DOC",
         sample_type == "Rack" | sample_type == "Grab" & sample == "Grab") %>%
  mutate(site = factor(site, exclude = "Lab"),
         site = factor(site)) %>% 
  ggplot(aes(x = NPOC_ppm, y = DOCeq_ppm, fill = two_seasons)) +  
  geom_jitter(shape = 21, size = 3, alpha = 0.6) +
  xlim(0, 20) +
  ylim(0, 20) +
  geom_abline(slope = 1, intercept = 0, lty = "dotted",) +  
  scale_fill_manual(values = c("#f4AB0E", "#09A4D2")) + 
  theme_bw() +
  theme(legend.position = "top") +
  labs(x = "DOC (mg/L as NPOC)", y = "CDOM (mg/L from UV-Vis) ", fill = "sampling season:",
       caption = "Fig.6 DOC concentration from direct measure versus CDOM from UV-Vis absorbance") 
```

Figure 7 shows the same DOC-CDOM comparison from Figure 6, isolated to the six sub-basin monitoring sites. The seasonal relationship appears similar for the six sites.

```{r, DOC-vs-CDOM-subbasins, echo = FALSE}
# six primary sites: DOC vs CDOM
sixfilter %>% filter(analysis == "DOC",
         sample_type == "Rack" | sample_type == "Grab" & sample == "Grab") %>%
  ggplot(aes(x = NPOC_ppm, y = DOCeq_ppm, fill = two_seasons)) +
  geom_jitter(shape = 21, size = 2, alpha = 0.6) +
  xlim(0, 20) +
  ylim(0, 20) +
  geom_abline(slope = 1, intercept = 0, lty = "dotted",) + 
  scale_fill_manual(values = c("#f4AB0E", "#09A4D2")) +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  theme_bw() +
  theme(legend.position = "top") +
  labs(x = "DOC (mg/L as NPOC)", y = "CDOM (mg/L from UV-Vis)", fill = "sampling season:",
       caption = "Fig.7 Six installation sites showing DOC concentration versus CDOM from UV-Vis absorbance")
#ggsave(path = "R-outputs_UBC-forWater-MSc_HMc/", filename = "Fig7_DOCvsCDOM_6sites_scatterplot.png") 
```

#### SUVA
In progress: analysis of spectral fingerprint data for slope ratio indices, which will help to elucidate seasonal DOM character shifts.

```{r, SUVA-plots-in-progress}

# SUVA vs time
sampleresults %>% 
  filter(sample_type == "Rack" | sample_type == "Grab", 
         analysis == "DOC") %>%
  mutate(site = factor(site, exclude = "Lab"),
         site = factor(site),
         trip_end = factor(trip_end)) %>% 
  ggplot(aes(x = trip_end, y = pseudoSUVA, fill = two_seasons)) +  
  geom_jitter(shape = 21, size = 3, alpha = 0.6) +
  scale_fill_manual(values = c("#f4AB0E", "#09A4D2")) +
  theme_bw() +
  ylim(0, 20) +
  theme(legend.position = "bottom",
       axis.text.x = element_text(angle = 90)) +
  labs(x = "", y = expression("SUVA "[254]), fill = "sampling season:",
       caption = "Specific UV-absorbance at 254nm ")



# --- UV-Vis parameters
# --- Spectrolyser data with TOCV data
sampleresults %>% 
  filter(sample_type == "Grab" & sample == "Grab",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = NPOC_ppm, y = NO3.Neq_ppm, fill = two_seasons)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  geom_abline(lty = "dotted", slope = 1, intercept = 0) +
  scale_fill_manual(values = c("#5B99CC", "#3B3838", "#f4AB0E")) +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "C-DOM (proxy DOC, mg/L)", y = "nitrate (mg/L)", fill = "sampling season:",
       caption = "Grab sample DOC and nitrate concentrations (via spectrophotometry)...")

# --- Spectrolyser data - SAC254_Abs.m vs SAC436_Abs.m
sampleresults %>% 
  filter(sample_type == "Grab" & sample == "Grab",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = SAC254_Abs.m, y = SAC436_Abs.m, fill = two_seasons)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  geom_abline(lty = "dotted", slope = 1, intercept = 0) +
  scale_fill_manual(values = c("#5B99CC", "#3B3838", "#f4AB0E")) +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "SAC254_Abs.m", y = "SAC436_Abs.m", fill = "sampling season:",
       caption = "Grab sample spectral concentrations (via spectrophotometry)...")

# --- Spectrolyser data - NPOC vs SAC254_Abs.m
sampleresults %>% 
  filter(sample_type == "Grab" & sample == "Grab",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = NPOC_ppm, y = SAC254_Abs.m, fill = two_seasons)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = c("#5B99CC", "#3B3838", "#f4AB0E")) +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "DOC (mg/L as NPOC)", y = "CDOM abs (SAC 254 /m)", fill = "sampling season:",
       caption = "Grab sample spectral concentrations (via spectrophotometry)...")



# all sites DOC versus SAC 254
sampleresults %>% 
  filter(sample_type == "Grab" & sample == "Grab") %>%
  ggplot(aes(x = NPOC_ppm, y = SAC254_Abs.m, fill = two_seasons)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = c("#5B99CC", "#3B3838", "#f4AB0E")) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "DOC (mg/L as NPOC)", y = "CDOM abs (SAC 254 /m)", fill = "sampling season:",
       caption = "Grab sample spectral concentrations (via spectrophotometry)...")


# --- RACK SAMPLES


# --- DOC versus CDOM on rack samples
sampleresults %>% 
  filter(sample_type == "Rack",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = NPOC_ppm, y = DOCeq_ppm, fill = sample)) +  
  geom_point(shape = 21, size = 2) +
  theme_bw() +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  viridis::scale_fill_viridis(discrete = TRUE) 
labs(x = "DOC (mg/L as NPOC)", y = "CDOM (mg/L)", fill = "Rack Position:",
     caption = "Rack sample DOC concentration based on direct (combustion measuring all non-purgeable organic carbon) and proxy (spectrophotometry measuring chromophoric fraction) methods of quantification...")

# --- DOC versus NO3- on rack samples
sampleresults %>% 
  filter(sample_type == "Rack",
         site == "Weeks-out" |
           site == "Leech-head" |
           site == "Chris-crk" |
           site == "Cragg-crk" |
           site == "West-Leech"| 
           site == "Tunnel") %>%
  mutate(site = factor(site, levels = c("Weeks-out", "Chris-crk", "Leech-head", "Cragg-crk", "West-Leech", "Tunnel"))) %>%
  ggplot(aes(x = NPOC_ppm, y = NO3.Neq_ppm, fill = sample)) +  # exchange NPOC_ppm with DOCeq_ppm -- similar pattern but split seasonally
  geom_point(shape = 21, size = 2) +
  theme_bw() +
  facet_wrap(~site, nrow = 3, ncol = 2) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(x = "DOC (mg/L as NPOC)", y = "nitrate (mg/L)", fill = "Rack Position:",
       caption = "Rack sample DOC and nitrate concentrations (via spectrophotometry)...")

# --- facet wrap scatter plots of conc --- ## W.I.P. ###
# DOC over time (by trip) -- try mutating in a month-year for clarity
sixfilter %>%
  filter(sample_type == "Rack" | sample_type == "Grab", 
         analysis == "DOC") %>% 
  mutate(trip = factor(trip, levels = (1:22))) %>% 
  ggplot(aes(x = trip, y = NPOC_ppm, fill = sample)) +
  geom_jitter(shape = 21, size = 2) +
  #facet_wrap(~site, ncol = 2, nrow = 3) +
  viridis::scale_fill_viridis(discrete = TRUE) 
  #geom_jitter() +
  #theme_bw() +
  #labs(y = "DOC (mg/L)", x = "time span", colour = "sample type:") +
  #theme(legend.position = "top",
  # axis.text.x = element_text(angle = 90))   # rotate tick labels for clarity
  
```

## FWx

### Rain Plots for Chris and Martin's Gulch 
```{r, rain-plots}

# Rn15 is 15-minute rainfall (mm) 
# Prec_1 is hourly accummulated precipitation (mm)
# Temp is 15 minute intervals (degrees C)
rainplot <- precip_data %>% 
  filter(StationName == "FWx Chris Creek" | StationName == "FWx Martins Gulch") %>% 
  mutate(date = lubridate::as_date(DateTime)) %>% 
  group_by(StationName, date) %>% 
  dplyr::summarise(daily_rn = sum(Rn_1, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  ggplot(aes(x = date, y = daily_rn)) +
  geom_col(colour = "#09A4D2") +
  scale_y_reverse() +
  labs(x = "", y = "rain (mm/day)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_blank()) +
  gghighlight::gghighlight(date >= "2018-10-23",
                           unhighlighted_params = list(colour = "#3B3838")) +
  facet_wrap(~StationName, nrow = 1)

# plot LWSA snow
snowplot <- precip_data %>% 
  filter(StationName == "FWx Chris Creek" | StationName == "FWx Martins Gulch") %>% 
  mutate(date = lubridate::as_date(DateTime)) %>% 
  group_by(StationName, date) %>% 
  dplyr::summarise(daily_Snowmean = mean(SnowDep, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  ggplot(aes(x = date, y = daily_Snowmean)) +
  geom_col(colour = "grey60") +
  labs(x = "", y = expression('snow depth (m /day)')) +
  theme_bw() +
  scale_x_discrete(labels = NULL) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  gghighlight::gghighlight(date >= "2018-10-23",
                           unhighlighted_params = list(colour = "#3B3838")) +
  facet_wrap(~StationName, nrow = 1) 

# plot LWSA temperature
tempplot <- precip_data %>% 
  filter(StationName == "FWx Chris Creek" | StationName == "FWx Martins Gulch") %>% 
  mutate(date = lubridate::as_date(DateTime)) %>% 
  group_by(StationName, date) %>% 
  dplyr::summarise(daily_Tmean = mean(Temp, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  ggplot(aes(x = date, y = daily_Tmean)) +
  geom_line(colour = "#f4AB0E") +
  geom_hline(yintercept = 0,
             linetype = "dotted") +
  labs(x = "", y = expression('mean daily air temp ('*~degree*C*')')) +
  theme_bw() +
  #scale_x_discrete(labels = NULL) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.text.x = element_text(angle = 90)) +
  gghighlight::gghighlight(date >= "2018-10-23",
                           unhighlighted_params = list(colour = "#3B3838")) +
  facet_wrap(~StationName, nrow = 1) 


# LWSA Wx -- stack precip and temp with cowplot
cowplot::plot_grid(rainplot, snowplot, tempplot, ncol = 1, align = "v",
                   rel_heights = c(1,1,1))

# save plot
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/Wx_LWSA.png")
```

### Mean LWSA weather
```{r, mean-weather}

# mean precip plot
mean_rainplot <- LWSA_meanWx %>% 
  mutate(date = lubridate::as_date(DateTime)) %>% 
  group_by(date) %>% 
  dplyr::summarise(daily_rn = sum(Rn_1_mean, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  ggplot(aes(x = date, y = daily_rn)) +
  geom_col(colour = "#09A4D2") +
  scale_y_reverse() +
  scale_x_discrete(labels = NULL) +
  labs(x = "", y = "LWSA mean rain (mm/day)") +
  theme_bw() +
  theme(legend.position = "none")+
  gghighlight::gghighlight(date >= "2018-10-23",
                           unhighlighted_params = list(colour = "#3B3838")) 

# plot LWSA snow
mean_snowplot <- LWSA_meanWx %>% 
  mutate(date = lubridate::as_date(DateTime)) %>% 
  group_by(date) %>% 
  dplyr::summarise(daily_Snowmean = mean(SnowDep_mean, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  ggplot(aes(x = date, y = daily_Snowmean)) +
  geom_col(colour = "grey60") +
  labs(x = "", y = expression('snow depth (m /day)')) +
  theme_bw() +
  scale_x_discrete(labels = NULL) +
  theme(legend.position = "none") +
  gghighlight::gghighlight(date >= "2018-10-23",
                           unhighlighted_params = list(colour = "#3B3838")) 

# plot LWSA temperature
mean_tempplot <- LWSA_meanWx %>% 
  mutate(date = lubridate::as_date(DateTime)) %>% 
  group_by(date) %>% 
  dplyr::summarise(daily_Tmean = mean(Temp_mean, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  ggplot(aes(x = date, y = daily_Tmean)) +
  geom_line(colour = "#f4AB0E") +
  geom_hline(yintercept = 0,
             linetype = "dotted") +
  labs(x = "", y = expression('Mean daily air temp ('*~degree*C*')')) +
  theme_bw() +
  #scale_x_discrete(labels = NULL) +
  theme(legend.position = "none") +
  gghighlight::gghighlight(date >= "2018-10-23",
                           unhighlighted_params = list(colour = "#3B3838")) 

# LWSA Wx -- stack precip and temp with cowplot
cowplot::plot_grid(mean_rainplot, mean_snowplot, mean_tempplot, ncol = 1, align = "v")

# save plot
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/Wx-means_LWSA.png")
```

### Wx data summaries
```{r, Wx-summaries}

# precip_data summary
precip_data %>%
  mutate(Year = lubridate::year(DateTime)) %>% 
  filter(StationName != "Survey Mtn Wx", 
         Year != 2017, Year != 2020) %>% 
  group_by(Year, StationName) %>%
  summarise(total_precip_mm = sum(Rn15, na.rm = TRUE),
            #mean_snow_m = mean(SnowDep, na.rm = TRUE), # not sure how to report
            annual_mean_temp = mean(Temp, na.rm = TRUE),
            temp_sd = sd(Temp, na.rm = TRUE)) %>% 
  dplyr::rename("year" = Year, 
                "station name" = StationName, 
                "annual precip. (mm)" = total_precip_mm,
                #"mean snow (m)" = mean_snow_m,
                "mean air temp. (°C)" = annual_mean_temp, 
                "stdev air temp. (± °C)" = temp_sd) %>% 
  write_csv("R-outputs_UBC-forWater-MSc_HMc/tables/Wx_LWSA-summary.csv")

# ---- nearby weather
# malahat weather
malahat_data <- read_csv("R-inputs_UBC-forWater-MSc_HMc/Malahat_station-data-11596.csv", 
                         skip = 16,
                         col_names = TRUE,
                         col_types = list("f", "c", "d", "d")) %>% 
  mutate(Datetime = lubridate::ymd_hms(Datetime, tz = TZ, truncated = 1),
         Date = lubridate::as_date(Datetime),
         Year = lubridate::year(Datetime))

# plot malahat rain and highlight my study period
malahat_rn <- malahat_data %>% 
  filter(Analysis == "Precipitation Amount (mm)") %>% 
  ggplot(aes(x = Datetime, y = Value)) +
  geom_col(colour = "#09A4D2") +
  scale_y_reverse() +
  labs(x = "", y = "rain (mm/day)") +
  theme_bw() +
  theme(legend.position = "none") +
  gghighlight::gghighlight(Datetime > "2018-10-23",
                           unhighlighted_params = list(colour = "#3B3838"))

# plot malahat temperature and highlight my study period
malahat_temp <- malahat_data %>% 
  filter(Analysis == "Temperature (Mean) (celsius)") %>% 
  ggplot(aes(x = Datetime, y = Value)) +
  geom_line(colour = "#f4AB0E") +
  geom_hline(yintercept = 0,
             linetype = "dotted") +
  labs(x = "", y = expression('Mean daily air temp ('*~degree*C*')')) +
  theme_bw() +
  gghighlight::gghighlight(Datetime > "2018-10-23",
                           unhighlighted_params = list(colour = "#3B3838"))

# stack with cowplot
cowplot::plot_grid(malahat_rn, malahat_temp, ncol = 1, align = "v")
# save plot
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/Wx_Malahat.png")

# malahat_data precip + air temp summary
malahat_data %>% 
  filter(Analysis == "Precipitation Amount (mm)", 
         between(Year, 2014, 2019)) %>% 
  group_by(Year) %>%
  summarise(total_precip = sum(Value, na.rm = TRUE)) %>% 
  right_join((
    malahat_data %>% 
      dplyr::filter(Analysis == "Temperature (Mean) (celsius)", 
                    between(Year, 2014, 2019)) %>% 
      group_by(Year) %>%
      summarise(annual_mean_temp = mean(Value, na.rm = TRUE),
                temp_sd = sd(Value))), 
    by = "Year") %>%
  dplyr::rename("year" = Year, 
                "annual precip. (mm)" = total_precip, 
                "mean air temp. (°C)" = annual_mean_temp, 
                "stdev air temp. (± °C)" = temp_sd) %>% 
  write_csv("R-outputs_UBC-forWater-MSc_HMc/tables/Wx_malahat-summary.csv")

# knitr::kable(digits = 1, col.names = c("Year", "mean temp. (°C)", "std.dev. (±°C)"))

```

```{r, Wx-Stn}
# I want to know precip totals over the study period
# by month and by season
# use rain to define storm events

# calculate total rainfall at each of the wx-stns (survey mountain went in in late)
rn_total <- precip_data %>% 
  group_by(StationName) %>% 
  dplyr::summarise(rain_MSc = sum(Rn_1, na.rm = TRUE)) %>% 
  ungroup() 
  
# monthly rainfalls
rn_monthly <- precip_data %>% 
  mutate(month = lubridate::month(DateTime),
         year = lubridate::year(DateTime)) %>%
  group_by(StationName, year, month) %>% 
  dplyr::summarise(rain_monthly = sum(Rn_1, na.rm = TRUE)) %>% 
  ungroup()

# annual rainfalls
rn_annual <- precip_data %>% 
  mutate(year = lubridate::year(DateTime)) %>%
  group_by(StationName, year) %>% 
  dplyr::summarise(rain_monthly = sum(Rn_1, na.rm = TRUE)) %>% 
  ungroup()

# mean annual and seasonal rainfalls
rn_seasonalAnnual <- precip_data %>% 
  mutate(year = lubridate::year(DateTime),
         month = lubridate::month(DateTime),
         season = case_when(
           between(month, 6, 9) ~ "dry",
           TRUE ~ "wet")) %>%
  group_by(StationName, year) %>% 
  dplyr::summarise(rain_monthly = sum(Rn_1, na.rm = TRUE),
                   rn = sum(rain_monthly, na.rm = TRUE)) %>% 
  ungroup()

# water-year rainfalls (Oct 1 - Sept 30)
rn_wateryr <- precip_data %>%
  group_by(StationName) %>% 
  mutate(month = lubridate::month(DateTime),
         year = lubridate::year(DateTime),
         water_year = case_when(
           between(month, 1, 9) & year == "2018" ~ "2018",
           between(month, 10, 12) & year == "2018" ~ "2019",
           between(month, 1, 9) & year == "2019" ~ "2019",
           between(month, 10, 12) & year == "2019" ~ "2020",
           between(month, 1, 9) & year == "2020" ~ "2020")) %>%
  ungroup() %>% 
  filter(water_year != "2018") %>% 
  group_by(StationName, water_year) %>% 
  dplyr::summarise(rain = sum(Rn_1, na.rm = TRUE)) %>% 
  ungroup()

# plots ---

# Rn15 is 15-minute rainfall (mm) 
# Prec_1 is hourly accummulated precipitation (mm)
# Temp is 15 minute intervals (degrees C)
rainplot <- precip_data %>% 
  filter(StationName == "FWx Chris Creek" | StationName == "FWx Martins Gulch") %>% 
  mutate(date = lubridate::as_date(DateTime)) %>% 
  group_by(StationName, date) %>% 
  dplyr::summarise(daily_rn = sum(Rn_1, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  
  ggplot(aes(x = date, y = daily_rn)) +
  geom_col(colour = "#09A4D2") +
  scale_y_reverse() +
  labs(x = "", y = "rain (mm/day)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) +
  facet_wrap(~StationName, nrow = 1)

# plot temperature
tempplot <- precip_data %>% 
  filter(StationName == "FWx Chris Creek" | StationName == "FWx Martins Gulch") %>% 
  mutate(date = lubridate::as_date(DateTime)) %>% 
  group_by(StationName, date) %>% 
  dplyr::summarise(daily_Tmean = mean(Temp, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  
  ggplot(aes(x = date, y = daily_Tmean)) +
  geom_line(colour = "#3B3838") +
  geom_hline(yintercept = 0,
             linetype = "dotted") +
  labs(x = "", y = expression('Mean daily air temp ('*~degree*C*')')) +
  theme_bw() +
  scale_x_discrete(labels = NULL) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  facet_wrap(~StationName, nrow = 1) 


# try a cowplot
cowplot::plot_grid(rainplot, tempplot, ncol = 1, align = "v")
```

### Malahat Wx

```{r, malahat-wx}

# plot malahat rain and highlight my study period
malahat_data <- read_csv("R-inputs_UBC-forWater-MSc_HMc/Malahat_station-data-11596.csv", 
                         skip = 16,
                        col_names = TRUE,
                        col_types = list("f", "c", "d", "d")) %>% 
  mutate(Datetime = lubridate::ymd_hms(Datetime, tz = TZ, truncated = 1),
         Date = lubridate::as_date(Datetime))

malahat_rn <- malahat_data %>% 
  filter(Analysis == "Precipitation Amount (mm)") %>% 
  ggplot(aes(x = Datetime, y = Value)) +
  geom_col(colour = "#09A4D2") +
  scale_y_reverse() +
  labs(x = "", y = "rain (mm/day)") +
  theme_bw() +
  #scale_x_discrete(labels = NULL) +
  theme(legend.position = "none") +
  gghighlight::gghighlight(Datetime > "2018-10-22",
                           unhighlighted_params = list(colour = "#3B3838"))

# plot malahat temperature and highligh my study period
malahat_temp <- malahat_data %>% 
  filter(Analysis == "Temperature (Mean) (celsius)") %>% 
  ggplot(aes(x = Datetime, y = Value)) +
  geom_line(colour = "#f4AB0E") +
  geom_hline(yintercept = 0,
             linetype = "dotted") +
  labs(x = "", y = expression('Mean daily air temp ('*~degree*C*')')) +
  theme_bw() +
  gghighlight::gghighlight(Datetime > "2018-10-22",
                           unhighlighted_params = list(colour = "#3B3838"))
  

# try a cowplot
cowplot::plot_grid(malahat_rn, malahat_temp, ncol = 1, align = "v")

# how much rain?
malahat_data %>% 
  mutate(year = lubridate::year(Datetime),
         month = lubridate::month(Datetime),
         season = case_when(
           between(month, 7, 9) ~ "dry",
           TRUE ~ "wet")) %>%
  group_by(season, year) %>% 
  dplyr::summarise(av_rn = sum(Value, na.rm = TRUE)) %>% 
  ungroup()

```

## River Stage

### Mega-Plot

Plot stage, precip, temp and snow and then create a one-page mega plot of all combined.

```{r, Wx-stage-megas-plots}
# plot 
# stage at each of the subbasins
stage_plot <- odyssey_data %>% 
  ggplot(aes(x = DateTime, y = corr_stage_cm))+
  geom_line(colour = "#09A4D2")+
  theme_bw()+
  facet_wrap(~source, ncol = 1, 
             scales = "free_y",
             strip.position = "right")+
  labs(y = "River Stage (cm)", x = "")+
  scale_x_datetime(date_breaks = "1.5 months", date_labels = "%Y-%m",
                   limits = ymd_hms(c("2018-10-24 00:00:00", "2020-01-31 00:00:00")))+
  theme(axis.text.x = element_text(angle = 90),
        plot.margin = unit(c(0,0,0,0), "cm")) # top, right, bottom, left)
# save plot
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/Wx_Stage-plot_subbasins.png")

# plot
# mean LWSA rain for study period
subbasin_meanrain_plot <- LWSA_meanWx %>% 
  mutate(date = lubridate::as_date(DateTime),
         Rain = factor("Rain")) %>% 
  group_by(date, Rain) %>% 
  dplyr::summarise(daily_rn = sum(Rn_1_mean, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  filter(date >= "2018-10-24") %>% 
  ggplot(aes(x = date, y = daily_rn)) +
  geom_col(aes(colour = Rain), colour = "#0072B2") +
  scale_y_reverse() +
  labs(x = "", y = "mm /day") +
  theme_bw() +
  #scale_x_date(date_breaks = "1.5 months", date_labels = "%Y-%m")+ # use to check alignment 
  scale_x_date(date_breaks = "1.5 months", labels = NULL)+  # remove axis labels when you're confident
  facet_wrap(~Rain, ncol = 1, 
             strip.position = "right") +
  theme(legend.position = "none",
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 90),
        plot.margin = unit(c(0,0,0,0), "cm")) # top, right, bottom, left)
# save plot
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/Wx_rain-plot_subbasins.png")

# plot 
# LWSA temp for the same time span
subasin_meantemp_plot <- LWSA_meanWx %>% 
  mutate(date = lubridate::as_date(DateTime),
         Temp = factor("Temp")) %>% 
  group_by(date, Temp) %>% 
  dplyr::summarise(daily_Tmean = mean(Temp_mean, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  filter(date >= "2018-10-24") %>% 
  ggplot(aes(x = date, y = daily_Tmean)) +
  geom_line(aes(colour = Temp), colour = "#E69F00") +
  geom_hline(yintercept = 0,
             linetype = "dotted") +
  labs(x = "", y = "°C /day") +
  theme_bw() +
  #scale_x_date(date_breaks = "1.5 months", date_labels = "%Y-%m")+ # use to check alignment 
  scale_x_date(date_breaks = "1.5 months", labels = NULL)+  # remove axis labels when you're confident
  facet_wrap(~Temp, ncol = 1, 
             strip.position = "right") +
  theme(legend.position = "none",
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 90),
        plot.margin = unit(c(0,0,0,0), "cm")) # top, right, bottom, left)
# save plot
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/Wx_temp-plot_subbasins.png")

# plot 
# LWSA snow for the same time span
subasin_snow_plot <- LWSA_meanWx %>% 
  mutate(date = lubridate::as_date(DateTime),
         Snow = factor("Snow")) %>% 
  group_by(date, Snow) %>% 
  dplyr::summarise(daily_meansnow = mean(SnowDep_mean, na.rm = TRUE)) %>% 
  ungroup()  %>% 
  filter(date >= "2018-10-24") %>% 
  ggplot(aes(x = date, y = daily_meansnow)) +
  geom_col(aes(colour = Snow), colour = "grey40") +
  labs(x = "", y = "m /day") +
  theme_bw() +
  #scale_x_date(date_breaks = "1.5 months", date_labels = "%Y-%m")+ # use to check alignment 
  scale_x_date(date_breaks = "1.5 months", labels = NULL)+  # remove axis labels when you're confident
  facet_wrap(~Snow, ncol = 1, 
             strip.position = "right") +
  theme(legend.position = "none",
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 90),
        plot.margin = unit(c(0.5,0,0,0), "cm")) # top, right, bottom, left
# save plot
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/Wx_snow-plot_subbasins.png")

# LWSA Wx -- stack precip and stage with cowplot
cowplot::plot_grid(subasin_snow_plot, subasin_meantemp_plot, subbasin_meanrain_plot, stage_plot, 
                   ncol = 1, 
                   axis = "l", 
                   align = "v",
                   rel_heights = c(2,2,2,10))
# save plot
ggsave("R-outputs_UBC-forWater-MSc_HMc/figures/Wx-stage_subbasins_megaplot.png",
       width = 8.5,
       height = 11,
       units = "in")

```

### normalized stage plots

The stage was normalized (min-max norm) to comapre relative rises
```{r, stage-plots}

# plot stage, lines over time
odyssey_data %>%
  group_by(source) %>% 
  dplyr::mutate(norm_stg = (stage_cm-min(stage_cm))/(max(stage_cm)-min(stage_cm))) %>% 
  ggplot(aes(x = DateTime, y = norm_stg))+
  geom_line(colour = "#0072B2") +
  #viridis::scale_colour_viridis(discrete = TRUE) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(y = "River stage (normalized)", x = "") +
  facet_wrap(~source, ncol = 1, strip.position = "right")


# plot stage, density ridges -- could be cool -- fix aesthetics 
odyssey_data %>%
  group_by(source) %>% 
  dplyr::mutate(norm_stg = (stage_cm-min(stage_cm))/(max(stage_cm)-min(stage_cm))) %>% 
  ggplot(aes(x = norm_stg, y = fct_rev(source)))+
  ggridges::geom_density_ridges(aes(fill = source), alpha = 0.6) +
  scale_fill_brewer(palette="Accent") +
  theme_bw() +
  scale_y_discrete() +
  theme(legend.position = "none")+
  labs(x = "River Stage (normalized)", y = "",
       caption = "Density distribution of min-max normalized stage at six subbasins")

```
