--- 
title: "Spatial and temporal variation in natural organic matter quantity (as dissolved organic carbon) and quality (via UV-Vis spectroscopy) across the Leech River watershed, a second growth forested drinking water supply area on Vancouver Island, BC"
author: "Hannah J. McSorley"
date: "2020"
site: bookdown::bookdown_site
output:
  bookdown::word_document2:
    lof: true
    lot: true
    toc: true
    toc-depth: 5
    fig_caption: yes
    reference_docx: UBC-RC_ThesisTemplate_V9_HMc-Template.docx
bibliography: library.bib
link-citations: yes
---

```{r index-setup, warning = FALSE, message=FALSE, include = FALSE, package.startup.message = FALSE}

knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE)

# load required packages
library(bookdown)
library(tidyverse)
library(readr)    # read in delimited files
library(knitr)    # for tidy tables

```

# Abstract  

_(max 350 words) - roman numeral TOC_


Key points:

* refined method of vertical Rack passive sampling of rising stage in streams
* there were seasonal differences in spatial patterns to NOM character, although the dry and wet season mean concentrations were the same.
* mixing and reservoir effects will change riverine water quality prior to intake at the tower

\  

...
Streams are intrinsically linked to their watersheds through dynamic biotic-abiotic interactions and hydroclimatic relationships; as a result, aqueous biogeochemicals like NOM represent an important link between ecosystem processes, land-use, hydrology, and water resources. These water-quality signatures are useful tracers to better understand catchment processes and regional hydrology, as they are indicative of flow paths, sources, chemical origins and transport pathways [@Abbott2018; @Meyer1983; @Vidon2008; @Rautu2019].  
...

\  

***to be updated following completion of results*** 

Monitoring source water quality and hydrologic dynamics is a crucial part of a multi-barrier approach to clean drinking water. 
In a riverine system, hydrochemical pulses have a range of magnitudes, timings and relationships amongst sub-catchments. 
As the majority of drinking water in Canada originates in forested headwaters, forest management is intimately tied to drinking water supplies for many communities. There are many ways in which forest management can effect the hydrology of a catchment, as well as the water quality. However, without a baseline understanding of hydrochemical dynamics, it's difficult to say whether observations fit within baseline variability or indicate a departure from a catchment's range due to forest prescriptions. 

As part of the NSERC 'forWater' Network for Forested Drinking Water Source Protection Technologies, this research was conducted in partnership with a regional protected water supply to characterize the relative ranges of hydrochemical dynamics and the syncrony of rainfall response among subbasins. Six subbasin sites were equipped with vertical sampling racks to continuously log river stage and passively collect water samples on the rising limb of the hydrograph. Samples were analyzed for dissolved organic carbon (DOC) and dissolved organic matter (DOM) through high temperature combustion and UV-Vis spectroscopy (respectively) to assess landscape connectivity, and a subset of samples were analyzed for a suite of metals to assess DOM transport relationships. 

As a case study, understanding the baseline of hydrochemical dynamics in this protected water supply area can help pave the way for future experimental forest treatments, such as preventative forest fuel management, and can help to anticipate changes in treatment requirements due to hydrodynamic forcing across the watershed. More broadly, these analyses add to our understanding of "natural" variability across a recently undisturbed second growth forested catchment.  

This research explored the spatial and temporal dynamics of hydrochemcial synchrony 


******************

Most drinking water in Canada originates in forested headwaters, therefore forest management is intimately tied to the quality and quantity of water supply for many communities. However, without a baseline understanding of a watershed’s hydrochemical dynamics, it is difficult to determine if observations indicate a departure from natural variance due to forest treatments, or if observations fall within baseline variation. This research was conducted in the Leech River Watershed (~96 km^2^, elevation 215 to 870 m a.s.l) which experienced extensive forest harvesting prior to 2007 and is designated as a future supplemental drinking water supply area for Greater Victoria, British Columbia, Canada. The primary objective of this study was to characterize the range of hydrochemical dynamics and the synchrony of rainfall responses among sub-basins ranging in size from 9.6 to 37 km^2^. Six sites were equipped with vertical racks to passively collect water samples on the rising limb of the hydrograph while measuring stream stage. Synoptic water sampling was completed every two to four weeks from November 2018 to February 2020. A total of 458 samples (204 Rack and 254 Synoptic Grab samples) were collected and analyzed for dissolved organic carbon (DOC) and dissolved organic matter (DOM). Additionally, a subset of 42 samples were analyzed for a suite of total metals to assess aqueous DOM transport relationships. Mean sub-basin DOC concentrations ranged from 7.4 ± 1.5 mg L^-1^ to 10.4 ± 3.6 mg L^-1^ (DOC range spanned 2.5 - 29.75 mg L^-1^). Across the Leech watershed, there was an overall reduction in DOC concentration from low to high order streams, and DOC concentrations decreased throughout the wet season (Oct-Mar). Concentrations of DOC exhibited a positive relationship with concentrations of several metals (R^2^ values for Hg: 0.99; Al: 0.81; Fe: 0.72; Cu: 0.47; Ba: 0.25; Mn: 0.21). Seasonal differences in DOM character were assessed by SUVA~254~ and other spectral indices derived from UV-Vis absorbance full-scan data. DOC concentration patterns during stormflow will be used to indicate whether DOC flux was driven by DOM supply limitation or hydrologic controls. Rainfall response will be discussed on a per-storm basis regarding response synchrony among sub-basins. This research establishes a baseline of hydrochemical dynamics across a water supply area where commercial forest management ceased more than a decade ago. These data may also be useful for future assessment of forest management strategies to reduce wildfire risk. Furthermore, results from this work will aid source water protection strategies when the Leech Water Supply Area becomes an active source for the Greater Victoria water supply via inter-basin transfer. 

# Lay Summary 

_(max 150 words) - roman numeral TOC_

***to be updated following completion of results*** 

This research contributes to understanding the variability in DOM and DOC across a forested riverine watershed: the Leech River watershed on Vancouver Island, British Columbia, Canada. Land-use impacts are controlled in this research area as 96% of the watershed is protected as drinking water supply area (Leech Water Supply Area). Like most forested areas on Vancouver Island, the Leech watershed is second-growth softwood forest with a history of extensive harvest (nearly 96% cleared).

Sixteen months of bi-weekly field work was completed with the goals of contributing to the characterization of the Leech Water Supply Area (LWSA) while furthering our understanding of the variability of dissolved organic matter (DOM) dynamics in hydrologic response across a second growth forested watershed. 

The purpose of this master's research project was to establish a baseline understanding of hydrologic responses and water quality variability in rivers across the LWSA. The approach includes advanced passive sampling within stormflow, supplemented with synoptic grab sampling between storm events and during summer baseflow. Discrete samples of river water were collected passively during the rising limb of stormflow using low-powered, low-cost, custom-built vertical rack samplers including water level loggers (Odyssey) and observational reference staff gauges. By collecting samples during stormflow, a more robust understanding of water quality dynamics was achieved than basic grab sampling alone. Using low-powered passive sampling techniques allowed for multiple (six) sites to be equipped with monitoring/sampling racks, providing spatial resolution of hydrochemical variability across the watershed. 

# Preface

_roman numeral TOC_

This dissertation is an original intellectual product of the author, Hannah J. McSorley. 

\  

Vertical sampling racks (Chapter 2) were based on principles employed by Maartje Korver (MSc Vrije Universiteit Amsterdam) at Hakai Institute, BC, Canada. Siphon sampling bottles were built by H.J. McSorley based on US Geological Survey's single-stage siphon sampler for suspended sediment design (USGS U-59 Sampler) and a prototype provided by M. Korver. 

\  

Laboratory analyses conducted at the University of British Columbia (UBC), and all data analysis (using R (R 3.6.2) in RStudio (Version 1.3.820)) were completed solely by H.J. McSorley. Most geospatial data were collected from the Government of Canada Geospatial Data Extraction tool (geogratis.gc.ca) with supplemental data provided by the Capital Regional District (CRD). Weather station data and geospatial data (landcover and subsurface geological layers) for the Leech Watershed was supplied by the CRD and used with their permission. All maps included in this thesis were created by H.J. McSorley using QGIS (version 3.12.1, Bucuresti; www.qgis.org); catchment boundaries were delineated using the QGIS GRASS plugin (GRASS GIS 7, version 2). Geospatial data extractions (Table 2 & Table 13) were completed or confirmed (in the case of watershed boundary delineation) by Alison Bishop, BSc, ADGIS (Research Assistant, VIU Coastal Hydrology Research Lab). 

\  

see: https://www.grad.ubc.ca/sites/default/files/doc/page/thesis_sample_prefaces.pdf

\  

* TOC
* LOT
* LOF

\  

```{r Abbreviations, echo = FALSE}
read_csv("R-inputs_UBC-forWater-MSc_HMc/tables/index-acronyms.csv", col_names = TRUE) %>%
  arrange(Acronym) %>% 
  knitr::kable(caption = "List of Abbreviations")
```

\  

```{r Glossary, echo = FALSE}
read_csv("R-inputs_UBC-forWater-MSc_HMc/tables/index-glossary.csv", col_names = TRUE) %>%
  arrange(Term) %>% 
  knitr::kable(caption = "Glossary of Terms")
```

\  

# Acknowledgments

This research work would not have been possible without the support and physical accommodations provided by the Capital Regional District (CRD) Watershed Protection and Management Division, Integrated Water Services (Victoria, BC). Thank you so much. I would like to acknowledge the help, support and assistance provided by the following CRD folks: Tobi Gardner, Kathy Haesevoats, Annette Constabel, Joel Ussery, Patrick McCoubrey, Ryan Biggs, Burn Hemus, Christoph Moch, Jessica Dupuis, Devon Barnes, and Athina Connor. I'm grateful to have been supported by the entire CRD Field Operations Staff; thank you all for making me feel welcome on site and including me in daily field operations and worker checks.

\  

This research also would not have been possible without support and encouragement from my academic supervisors, Bill Floyd and Mark Johnson -- thank you both for your patience, for supporting me, and for helping me grow as a researcher and writer; it's been challenging and truly wonderful. Thank you also to academic partners in the NSERC forWater Network: Suzanne Tank, Mike Stone, Dana Harriman, Monica Emelko, Uldis Silins, and Axel Anderson. Thank you all for interesting discussions and your feedback. I'm grateful to the entire forWater Network for providing transdisciplinary training and workshops. Thank you to Emily Mistick for being my forWater travel buddy, for bouncing ideas and concepts around with me, and for checking my writing, each forWater trip was better with you there.

\  

I would like to acknowledge Vancouver Island University, University of British Columbia, the NSERC Canadian Graduate Scholarship Masters Award, and the NSERC forWater Network for Source Water Protection Strategies -- thank you for supporting me financial (and tangibly) as a master's student.   

\  

For help with field installations, streamflow gauging and sampling, a big thanks to my friend and former field partner, Stewart Butler (formerly of VIU Coastal Hydrology Research Lab); thanks Stew for being the best field partner on the coldest, wettest, darkest field days. Thanks also to Alison Bishop for assistance on a field trip during the winter of 2019/2020 and for so much help with GIS. I owe you both some beers.

\  

Big thanks to my incredibly wonderful friends and family for supporting me in my scientific and academic pursuits. I really appreciate all the love and support, dinners, coffees, bike rides, beers, proof-reading and encouragement. Thank you all for your patience also, this was a big project.

\  

__Land Acknowledgment__

The author, Hannah J. McSorley, acknowledges and thanks the First Nations on whose traditional lands she traveled, learned, researched, lived and played on during this master's thesis project, and on whose land she continues to live.

\  

The research sites in Greater Victoria water supply areas are located on traditional territory of the T’sou-ke (Sooke) Nation, who have lived on these lands since time immemorial and who were the original watershed protectors. The Capital Regional District occupies land of the Scia'new (Beecher Bay), Songhees, T’Sou-ke First Nation and Malahat First Nation.

\  

Research at the University of British Columbia in Vancouver BC was conducted on the traditional, unceded territories of xʷməθkʷəy̓əm (Musqueam) People. For the duration of this master's research, Hannah gratefully lived and played in East Vancouver on traditional territory of the Musqueam, Sḵwx̱wú7mesh (Squamish), and Səlilwətaɬ (Tsleil-Waututh) Nations. Traveling between UBC and the water supply areas included passage across Tsawout and Tsawwassen First Nation territories. 

\  

Vancouver Island University (Nanaimo campus) is located on traditional lands of the Snuneymuxw First Nation, Quw’utsun and Tla’Amin Peoples. The land traveled between VIU and the research sites, along the south east coast of Vancouver Island, includes territories of the Stz'uminus First Nation (Chemainus), Halalt, Cowichan Tribes, Malahat First Nation, T'Sou-ke First Nation, and Songhees.

\  

Thank you to the First Nations who are the original land protectors of the areas I call home; I tread lightly, and I am actively un-learning and re-learning our history.

\  

# Dedication

First, I dedicate this thesis to each person who reads it in its entirety.

\  

Second, I dedicate this thesis to the love of data science. I'm grateful for Jenny Bryan's online resources, Stack Overflow (stackoverflow.com) for the solution to so many coding challenges, and to Dan Moore for teaching me R (UBC GEOB 503) and continuing to support my R development with additional resources. Thank you to RStudio for making a functional and friendly IDE for the R programming language and to GitHub for making version control streamlined and reproducible. Cheers to Hadley Wickham for the tidyverse and Yihui Xie for the bookdown package (in which I generated this thesis).

\  

Third, I dedicate this to my undergraduate research supervisor and mentor, Dr. Erik Krogh (VIU Chemistry), for inspiring me to realize my potential as a scientific researcher. 

\  

Cheers!
