--- 
title: "Spatial and temporal variation in natural organic matter quantity (as dissolved organic carbon) and quality (via UV-Vis spectroscopy) across a second growth forested drinking water supply area on Vancouver Island, BC"
author: "Hannah J. McSorley"
date: "December 2020"
site: bookdown::bookdown_site
output:
  bookdown::word_document2:
    lof: true
    lot: true
    toc: true
    toc-depth: 5
    fig_caption: yes
    reference_docx: UBC-RC_ThesisTemplate_V9_HMc-Template.docx
bibliography: library.bib
link-citations: yes
---

```{r index-setup, warning = FALSE, message=FALSE, include = FALSE, package.startup.message = FALSE}

knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE)

# load required packages
library(bookdown)
library(tidyverse)
library(readr)    # read in delimited files
library(knitr)    # for tidy tables

```

# Abstract  

_(max 350 words) - roman numeral TOC_


Most drinking water in Canada originates in forested headwaters, therefore forest management is intimately tied to the quality and quantity of water supply for many communities. However, without a baseline understanding of a watershed’s hydrochemical dynamics, it is difficult to determine if observations indicate a departure from natural variance due to forest treatments, or if observations fall within baseline variation. Monitoring source water quality and hydrologic dynamics is a crucial part of a multi-barrier approach to clean drinking water. This research established a stream water sampling program across a second-growth forested drinking water supply area (Greater Victoria, British Columbia, Canada) to evaluate spatial and temporal patterns and variance in natural organic matter (NOM), a master variable in aquatic systems.  Over sixteen months (October 2018 to February 2020), 426 stream water samples were collected from twelve sites (ranging in size from 9.6 to 37 km^2^, elevation 215 to 870 m a.s.l) and were measured for NOM quality (via UV-Vis absorbance parameters) and quantity (as dissolved organic carbon, DOC). Mean sub-basin DOC concentrations ranged from 4.2 ± 1.8 mg L^-1^ to 9.9 ± 3.4 mg L^-1^ (DOC range spanned 1.64 - 19.1 mg L^-1^). From upstream to downstream NOM quantity and reactive character decreased. There was a seasonal shift in NOM character, from predominantly aliphatic in the dry season to predominantly aromatic in the wet season. Antecedent wetness was important for stream NOM molecular quality, and hydrologic connectivity to terrestrial source pools increased throughout the wet season. Approximately 80% of the time, DOC concentration peaked with stage. Early wet season NOM was not stable when held for 11 days (should be analyzed immediately), whereas the more aromatic, allochthonous NOM found in mid to late wet season samples was stable up to 20 days at temperatures between 0-7° C. DOC concentration was loosely correlated to air temperature, with higher concentrations occurring at warmer temperatures and lower concentrations occurring at lower temperatures; and freezing changed NOM molecular attributes in samples. Sub-sets of samples were evaluated for drinking water treatability parameters (n = 8) and total metals contents (n = 42). Dissolved organic carbon (DOC) concentration was well correlated with several metals  (R^2^ values for Hg: 0.99; Al: 0.81; Fe: 0.72; Cu: 0.47; Ba: 0.25; Mn: 0.21), evidence that NOM is indeed a master variable important in contaminant transport. Evaluation of treatability data with UV-Vis spectroscopic results revealed the spectral absorbance coefficient at 254 nm (SAC254) was a better indicator of disinfection byproduct formation potential (DBP-FP) than was DOC concentration or specific UV absorbance at 254 nm (SUVA254). SAC254 was well correlated with total trihalomethanes (r = 0.9882) and total haloacetic acids (HAAs, r = 0.9927), but was only weakly correlated to bromodichloromethane (BDCM, r = 0.6539). Six sites in the Leech River watershed (~96 km^2^), future supplemental drinking water supply area, were studied with vertical passive sampling racks to evaluate aqueous NOM dynamics on the rising hydrograph limb. Random Forest variable importance measure (RF VIM) evaluation of monitoring site data identified warm and wet conditions as key drivers for NOM dynamics. RF VIM showed that forest age and harvest history were important predictor variables for NOM aromaticity and molecular size but determined that subsurface parent material was a more important driver for NOM quantity and quality. Results were framed in context of continued water quality monitoring and planning for drinking water supply and future inter-basin transfers.


# Lay Summary 

_(max 150 words) - roman numeral TOC_

***to be updated following completion of abstract*** 

This research contributes to understanding the variability in DOM and DOC across a forested riverine watershed: the Leech River watershed on Vancouver Island, British Columbia, Canada. Land-use impacts are controlled in this research area as 96% of the watershed is protected as drinking water supply area (Leech Water Supply Area). Like most forested areas on Vancouver Island, the Leech watershed is second-growth softwood forest with a history of extensive harvest (nearly 96% cleared).

Sixteen months of bi-weekly field work was completed with the goals of contributing to the characterization of the Leech Water Supply Area (LWSA) while furthering our understanding of the variability of dissolved organic matter (DOM) dynamics in hydrologic response across a second growth forested watershed. 

The purpose of this master's research project was to establish a baseline understanding of hydrologic responses and water quality variability in rivers across the LWSA. The approach includes advanced passive sampling within stormflow, supplemented with synoptic grab sampling between storm events and during summer baseflow. Discrete samples of river water were collected passively during the rising limb of stormflow using low-powered, low-cost, custom-built vertical rack samplers including water level loggers (Odyssey) and observational reference staff gauges. By collecting samples during stormflow, a more robust understanding of water quality dynamics was achieved than basic grab sampling alone. Using low-powered passive sampling techniques allowed for multiple (six) sites to be equipped with monitoring/sampling racks, providing spatial resolution of hydrochemical variability across the watershed. 

# Preface

_roman numeral TOC_

This dissertation is an original intellectual product of the author, Hannah J. McSorley. 

\  

Vertical sampling racks (Chapter 2) were based on principles employed by Maartje Korver (MSc Vrije Universiteit Amsterdam) at Hakai Institute, BC, Canada. Siphon sampling bottles were built by H.J. McSorley based on US Geological Survey's single-stage siphon sampler for suspended sediment design (USGS U-59 Sampler) and a prototype provided by M. Korver. 

\  

Laboratory analyses conducted at the University of British Columbia (UBC), and all data analysis (using R (R 3.6.2) in RStudio (Version 1.3.820)) were completed solely by H.J. McSorley. Most geospatial data were collected from the Government of Canada Geospatial Data Extraction tool (geogratis.gc.ca) with supplemental data provided by the Capital Regional District (CRD). Weather station data and geospatial data (landcover and subsurface geological layers) for the Leech Watershed was supplied by the CRD and used with their permission. All maps included in this thesis were created by H.J. McSorley using QGIS (version 3.12.1, Bucuresti; www.qgis.org); catchment boundaries were delineated using the QGIS GRASS plugin (GRASS GIS 7, version 2). Geospatial data extractions (Table 2 & Table 13) were completed or confirmed (in the case of watershed boundary delineation) by Alison Bishop, BSc, ADGIS (Research Assistant, VIU Coastal Hydrology Research Lab). 

\  

see: https://www.grad.ubc.ca/sites/default/files/doc/page/thesis_sample_prefaces.pdf

\  

* TOC
* LOT
* LOF

\  

```{r Abbreviations, echo = FALSE}
read_csv("R-inputs_UBC-forWater-MSc_HMc/tables/index-acronyms.csv", col_names = TRUE) %>%
  arrange(Acronym) %>% 
  knitr::kable(caption = "List of Abbreviations")
```

\  

```{r Glossary, echo = FALSE}
read_csv("R-inputs_UBC-forWater-MSc_HMc/tables/index-glossary.csv", col_names = TRUE) %>%
  arrange(Term) %>% 
  knitr::kable(caption = "Glossary of Terms")
```

\  

# Acknowledgments

This research work would not have been possible without the support and physical accommodations provided by the Capital Regional District (CRD) Watershed Protection and Management Division, Integrated Water Services (Victoria, BC). Thank you so much. I would like to acknowledge the help, support and assistance provided by the following CRD folks: Tobi Gardner, Kathy Haesevoats, Annette Constabel, Joel Ussery, Patrick McCoubrey, Ryan Biggs, Burn Hemus, Christoph Moch, Jessica Dupuis, Devon Barnes, and Athina Connor. I'm grateful to have been supported by the entire CRD Field Operations Staff; thank you all for making me feel welcome on site and including me in daily field operations and worker checks.

\  

This research also would not have been possible without support and encouragement from my academic supervisors, Bill Floyd and Mark Johnson -- thank you both for your patience, for supporting me, and for helping me grow as a researcher and writer; it's been challenging and truly wonderful. Thank you also to academic partners in the NSERC forWater Network: Suzanne Tank, Mike Stone, Dana Harriman, Monica Emelko, Uldis Silins, and Axel Anderson. Thank you all for interesting discussions and your feedback. I'm grateful to the entire forWater Network for providing transdisciplinary training and workshops. Thank you to Emily Mistick for being my forWater travel buddy, for bouncing ideas and concepts around with me, and for checking my writing, each forWater trip was better with you there.

\  

I would like to acknowledge Vancouver Island University, University of British Columbia, the NSERC Canadian Graduate Scholarship Masters Award, and the NSERC forWater Network for Source Water Protection Strategies -- thank you for supporting me financial (and tangibly) as a master's student.   

\  

For help with field installations, streamflow gauging and sampling, a big thanks to my friend and former field partner, Stewart Butler (formerly of VIU Coastal Hydrology Research Lab); thanks Stew for being the best field partner on the coldest, wettest, darkest field days. Thanks also to Alison Bishop for assistance on a field trip during the winter of 2019/2020 and for so much help with GIS. I owe you both some beers.

\  

Big thanks to my incredibly wonderful friends and family for supporting me in my scientific and academic pursuits. I really appreciate all the love and support, dinners, coffees, bike rides, beers, proof-reading and encouragement. Thank you all for your patience also, this was a big project.

\  

__Land Acknowledgment__

The author, Hannah J. McSorley, acknowledges and thanks the First Nations on whose traditional lands she traveled, learned, researched, lived and played on during this master's thesis project, and on whose land she continues to live.

\  

The research sites in Greater Victoria water supply areas are located on traditional territory of the T’sou-ke (Sooke) Nation, who have lived on these lands since time immemorial and who were the original watershed protectors. The Capital Regional District occupies land of the Scia'new (Beecher Bay), Songhees, T’Sou-ke First Nation and Malahat First Nation.

\  

Research at the University of British Columbia in Vancouver BC was conducted on the traditional, unceded territories of xʷməθkʷəy̓əm (Musqueam) People. For the duration of this master's research, Hannah gratefully lived and played in East Vancouver on traditional territory of the Musqueam, Sḵwx̱wú7mesh (Squamish), and Səlilwətaɬ (Tsleil-Waututh) Nations. Traveling between UBC and the water supply areas included passage across Tsawout and Tsawwassen First Nation territories. 

\  

Vancouver Island University (Nanaimo campus) is located on traditional lands of the Snuneymuxw First Nation, Quw’utsun and Tla’Amin Peoples. The land traveled between VIU and the research sites, along the south east coast of Vancouver Island, includes territories of the Stz'uminus First Nation (Chemainus), Halalt, Cowichan Tribes, Malahat First Nation, T'Sou-ke First Nation, and Songhees.

\  

Thank you to the First Nations who are the original land protectors of the areas I call home; I tread lightly, and I am actively un-learning and re-learning our history.

\  

# Dedication

First, I dedicate this thesis to each person who reads it in its entirety.

\  

Second, I dedicate this thesis to the love of data science. I'm grateful for Jenny Bryan's online resources, Stack Overflow (stackoverflow.com) for the solution to so many coding challenges, and to Dan Moore for teaching me R (UBC GEOB 503) and continuing to support my R development with additional resources. Thank you to RStudio for making a functional and friendly IDE for the R programming language and to GitHub for making version control streamlined and reproducible. Cheers to Hadley Wickham for the tidyverse and Yihui Xie for the bookdown package (in which I generated this thesis).

\  

Third, I dedicate this to my undergraduate research supervisor and mentor, Dr. Erik Krogh (VIU Chemistry), for inspiring me to realize my potential as a scientific researcher. 

\  

Cheers!
