--- 
title: " 'Spatial and temporal variation in dissolved organic carbon across a second growth forested watershed on Vancouver Island, BC' OR 'Quantifying synchrony and variability in source water quality across nested catchments of a protected second growth forested water supply area' "
author: "Hannah J. McSorley"
date: "2020"
site: bookdown::bookdown_site
output:
  bookdown::word_document2:
    lof: true
    lot: true
    toc: true
    fig_caption: true
    reference_docx: UBC-ThesisTemplate_HMc.docx
bibliography: library.bib
link-citations: yes
---

```{r index-setup, warning = FALSE, message=FALSE, include = FALSE, package.startup.message = FALSE}

knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE)

# load required packages
library(bookdown)
library(tidyverse)
library(readr)    # read in delimited files
library(knitr)    # for tidy tables

```

# Abstract  

_(max 350 words) - roman numeral TOC_

* to be updated following completion of results 

Most drinking water in Canada originates in forested headwaters, therefore forest management is intimately tied to the quality and quantity of water supply for many communities. However, without a baseline understanding of a watershed’s hydrochemical dynamics, it is difficult to determine if observations indicate a departure from natural variance due to forest treatments, or if observations fall within baseline variation. This research was conducted in the Leech River Watershed (~96 km^2^, elevation 215 to 870 m a.s.l) which experienced extensive forest harvesting prior to 2007 and is designated as a future supplemental drinking water supply area for Greater Victoria, British Columbia, Canada. The primary objective of this study was to characterize the range of hydrochemical dynamics and the synchrony of rainfall responses among sub-basins ranging in size from 9.6 to 37 km^2^. Six sites were equipped with vertical racks to passively collect water samples on the rising limb of the hydrograph while measuring stream stage. Synoptic water sampling was completed every two to four weeks from November 2018 to February 2020. A total of 458 samples (204 Rack and 254 Synoptic Grab samples) were collected and analyzed for dissolved organic carbon (DOC) and dissolved organic matter (DOM). Additionally, a subset of 42 samples were analyzed for a suite of total metals to assess aqueous DOM transport relationships. Mean sub-basin DOC concentrations ranged from 7.4 ± 1.5 mg L^-1^ to 10.4 ± 3.6 mg L^-1^ (DOC range spanned 2.5 - 29.75 mg L^-1^). Across the Leech watershed, there was an overall reduction in DOC concentration from low to high order streams, and DOC concentrations decreased throughout the wet season (Oct-Mar). Concentrations of DOC exhibited a positive relationship with concentrations of several metals (R2 values for Hg: 0.99; Al: 0.81; Fe: 0.72; Cu: 0.47; Ba: 0.25; Mn: 0.21). Seasonal differences in DOM character were assessed by SUVA~254~ and other spectral indices derived from UV-Vis absorbance full-scan data. DOC concentration patterns during stormflow will be used to indicate whether DOC flux was driven by DOM supply limitation or hydrologic controls. Rainfall response will be discussed on a per-storm basis regarding response synchrony among sub-basins. This research establishes a baseline of hydrochemical dynamics across a water supply area where commercial forest management ceased more than a decade ago. These data may also be useful for future assessment of forest management strategies to reduce wildfire risk. Furthermore, results from this work will aid source water protection strategies when the Leech Water Supply Area becomes an active source for the Greater Victoria water supply via inter-basin transfer. objective

# Lay Summary 

_(max 150 words) - roman numeral TOC_

This research contributes to understanding the variability in DOM and DOC across a forested riverine watershed: the Leech River watershed on Vancouver Island, British Columbia, Canada. Land-use impacts are controlled in this research area as 96% of the watershed is protected as drinking water supply area (Leech Water Supply Area). Like most forested areas on Vancouver Island, the Leech watershed is second-growth softwood forest with a history of extensive harvest (nearly 96% cleared).

The purpose of this master's research project was to establish a baseline understanding of hydrologic responses and water quality variability in rivers across the LWSA. The approach includes advanced passive sampling within stormflow, supplemented with synoptic grab sampling between storm events and during summer baseflow. Discrete samples of river water were collected passively during the rising limb of stormflow using low-powered, low-cost, custom-built vertical rack samplers including water level loggers (Odyssey) and observational reference staff gauges. By collecting samples during stormflow, a more robust understanding of water quality dynamics was achieved than basic grab sampling alone. Using low-powered passive sampling techniques allowed for multiple (six) sites to be equipped with monitoring/sampling racks, providing spatial resolution of hydrochemical variability across the watershed. 

# Preface

_roman numeral TOC_

This dissertation is an original intellectual product of the author, Hannah J. McSorley. 

The vertical sampling racks (Chapters 2 & 3) were based on principals employed by Maartje Korver (MSc Vrije Universiteit Amsterdam) at Hakai Institute, BC, Canada. The siphon sampling bottles were built by H.J.McSorley based on M.Korver's prototypes and the US Geological Survey's single-stage siphon sampler for suspended sediment design (USGS U-59 Sampler). 

Weather station data and geospatial data (forests and subsurface geological layers) for the Leech Watershed was supplied by the Capital Regional District and used with their permission.

All data analysis was completed by H.J.McSorley. All geospatial data extraction (Chapter 2, Table #####) was completed by (or confirmed by, in the case of watershed boundary delineation) Ali Bishop, BSc, ADGIS (Research Assistant, VIU Coastal Hydrology Research Lab). 

see: https://www.grad.ubc.ca/sites/default/files/doc/page/thesis_sample_prefaces.pdf

\  

* TOC
* LOT
* LOF

\  
```{r Abbreviations, echo = FALSE}
read_csv("R-inputs_UBC-forWater-MSc_HMc/index-acronyms.csv", col_names = TRUE) %>%
  arrange(Acronym) %>% 
  knitr::kable(caption = "**List of Abbreviations**")
```

\  

# Acknowledgments

This research work would not have been possible without the support and accommodation of the Capital Regional District (CRD) Watershed Protection and Management Division, Integrated Water Services (IWS) (Victoria, BC). I would like to acknowledge the help, support and assistance provided by the following CRD folks: Tobi Gardner, Annette Constabel, Kathy Haesevoats, Joel Ussery, Patrick McCoubrey, Ryan Biggs, Burn Hemus, Christoph Moch, Jessica Dupuis, Devon Barnes, and Athina Connor. I'm grateful to have been supported by the entire CRD Field Operations Staff; thank you all for making me feel welcome on site and including me in daily field operations. 

This research also would not have been possible without the support and encouragement from academic supervisors and partners from the NSERC forWater Network for Forested Drinking Water Source Protection Technologies: Bill Floyd, Mark Johnson, Suzanne Tank, Mike Stone, Dana Harriman, Monica Emelko, Uldis Silins, Axel Anderson. I would like to acknowledge the support from Vancouver Island University and University of British Columbia - thank you for supporting me as a master's student.  

For help with field installations and streamflow gauging, a big thanks to my friend and former field partner, Stewart Butler (VIU Coastal Hydrology Research Lab); thanks Stew. Thanks also to Alison Bishop for field assistance during the winter of 2019/2020, and for help with GIS.

Last but certainly not least, thanks to my incredibly wonderful friends and family for supporting me in my scientific and academic pursuits. I really appreciate all the love and support, dinners and coffees, bike rides and beers, proof-reading and encouragement. Thank you all for your patience also, this was a big project. 

\  

# Dedication

First, I dedicate this thesis to each person who reads it in its entirety.

Second, I dedicate this thesis to the love of data science. I'm grateful for Jenny Bryan's online resources, Stack Overflow (stackoverflow.com) for the solution to so many coding challenges, and to Dan Moore for teaching me R (UBC GEOB 503) and continuing to support my R development with additional resources. Thank you to RStudio for making a functional and friendly IDE for the R programming language and to GitHub for making version control streamlined and reproducible. Cheers to Hadley Wickham for the tidyverse and Yihui Xie for the bookdown package (in which I generated this thesis).

Third, I dedicate this to my undergraduate research supervisor and mentor, Erik Krogh (VIU Chemistry), for inspiring me to realize my potential as a scientific researcher. 

Cheers

