--- 
title: "Quantifying synchrony and variability in source water quality across nested catchments of a protected second growth forested water supply area "
author: "Hannah J. McSorley"
date: "April 2020"
site: bookdown::bookdown_site
output:
  bookdown::word_document2:
    lof: true
    lot: true
    toc: true
    fig_caption: yes
    reference_docx: word-styles-document_thesis.docx
bibliography: library.bib 
link-citations: yes
---

```{r index setup, warning = FALSE, include = FALSE, package.startup.message = FALSE}

knitr::opts_chunk$set(warning = FALSE, fig.align = "center")

# load required packages
library(bookdown)
library(tidyverse)
library(readr)    # read in delimited files
library(knitr)    # for tidy tables

```

# Abstract  (max 350 words) - roman numeral TOC

This research contributes to understanding the "natural" variability in DOM and DOC across a forested riverine watershed: the Leech River watershed on Vancouver Island, British Columbia, Canada. Land-use impacts are minimal in this research area as 96% of the watershed is protected as drinking water supply area (Leech Water Supply Area). Like most forested areas on Vancouver Island, the Leech watershed is second-growth softwood forest with a history of extensive harvest (nearly 96% cleared).

The purpose of this master's research project was to establish a baseline understanding of hydrologic responses and water quality variability in rivers across the LWSA. The approach includes advanced synoptic sampling within stormflow, supplemented with standard grab samples between storm events and during summer baseflow. Discrete samples of river water were collected passively during the rising limb of stormflow (falling limb prototype in progress) using low-powered, low-cost, custom-built vertical rack samplers including water level loggers (Odyssey) and observational reference staff gauges. By collecting samples during stormflow, a more robust understanding of water quality dynamics was achieved than basic grab sampling alone. Using low-powered passive sampling techniques allowed for multiple (six) sites to be equipped with monitoring/sampling racks, providing fairly good spatial resolution of hydrochemical variability across the watershed. 

# Lay Summary (max 150 words) - roman numeral TOC

include plain-language summary

# Preface  - roman numeral TOC

see: https://www.grad.ubc.ca/sites/default/files/doc/page/thesis_sample_prefaces.pdf

*TOC follows, then LOT, LOF, List of Illustrations, list of abbreviations

```{r Abbreviations, echo = FALSE}

read_csv("R-inputs_UBC-forWater-MSc_HMc/index-acronyms.csv", col_names = TRUE) %>% 
  knitr::kable()

```

# Acknowledgments

This research work would not have been possible without the support and accommodation of the Capital Regional District (CRD) Watershed Protection and Management Division, Integrated Water Services (IWS) (Victoria, BC). I would like to acknowledge the help, support and assistance provided by the following CRD people: Tobi Gardner, Annette Constabel, Kathy Haesevoats, Joel Ussery, Ryan Biggs, Patrick McCoubrey, Burn Hemus, Christoph Moch, Jessica Dupuis, and Devon Barnes.  

I'm grateful to have been supported by the entire CRD Field Operations Staff, thanks for making me feel welcome and included on site.  
  
This research also would not have been possible without the support and encouragement from academic supervisors and partners from the NSERC forWater Network for Forested Drinking Water Source Protection Technologies: Bill Floyd, Mark Johnson, Suzanne Tank, Mike Stone, Dana Harriman, Monica Emelko, Uldis Silins, Axel Anderson.  

For help with field installations and streamflow gauging, a big thanks to my former field partner, Stewart Butler, of Bill Floyd's Coastal Hydrology Research Lab; thanks Stew. Thanks also to Alison Bishop for field assistance during the winter of 2019/2020.    

Last but certainly not least, thanks to my wonderful friends and family for supporting me in my scientific and academic pursuits. I really appreciate all the love and support, bike rides and beers, proof-reading and encouragement. 

# Dedication

To each person who reads this thesis in its entirety.

For the love of data science, I am grateful for Jenny Byran's online resources, StackOverflow (http://stackoverflow.com) for the solution to so many coding challenges. Thank you to RStudio for making a functional and friendly IDE for the R programming language and to GitHub for making version control streamlined and reproducible. Cheers to Hadley Wickham for the tidyverse and Yihui Xie for the bookdown package (in which I generated this thesis).
