---
title: "Rodolfo spectrolyser data"
output: html_notebook
---

Notebook to do the following:
1. merge all .fp spectrolyser files into one file; repeat for .par files
2. run functions to generate indices; append these to .par files
3. apply statistics 

Improvements:
0. How to get less verbose info from purrr functions?
1. redo the slope ratio fuction using purrr to speed up

```{r data aggregation}
knitr::opts_chunk$set(tidy = TRUE, warning = FALSE)
library(tidyverse)
data_path <- "/Users/emilymistick/Google Drive/forWater Mistick/MKRF_results/K_spectro/FP_test"   # path to the data
files <- dir(data_path, pattern = "*.fp", recursive = TRUE, full.names = TRUE) # get file names

# fingerprint data
data <- files %>%
  map(~ read_delim(.,skip=1, delim = "\t"), quiet = TRUE) %>% 
  reduce(rbind)
library(lubridate)
data$spectroTime <- ymd_hms(data$`Date/Time`)
data <- data[order(data$spectroTime),] 

# derived parameter data
par.columns <- c("Timestamp","Status","Turb.FTU","Turb.status","NO3.N","NO3.status","TOC","TOC.status","DOC","DOC.status","Color.Tru","Color.Tru.status","Color.App","Color.App.status","SAC254","SAC254.status","Junk1","Junk2")

param.files <- dir(data_path, pattern = "*.par", recursive = TRUE, full.names = TRUE) # get file names
param.data <- param.files %>%
  map(~ read_delim(.,skip=2, na = "NaN",col_names=par.columns, delim = "\t")) %>% 
  reduce(rbind)
param.data

```

Now need to run functions over data to generate indices
```{r DOM indices}
#From Spencer 2007 (DOI: 10.1002/hyp.6887): A steep spectral slope (e.g. closer to 0.02) indicates low molecular weight material or decreasing aromaticity while a shallower spectral slope (e.g. closer to 0.01) indicates humic-like or higher molecular weight material with a higher aromatic content (Blough and Del Vecchio, 2002).

library(nlmrt)
calculate.SR <- function(x) {
  S1.alpha <- x[c(33:41)] # 275nm - 295nm
  S3.alpha <- x[c(63:83)] # 350nm - 400nm
  
  # S1 = nonlinear fit of an exponential function for S over n275 - n295
  y <- as.numeric(unlist(S1.alpha)) #EM added "unlist"
  X <- seq(275,295,2.5)
  temp <- data.frame(y=y,x=X)
  temp <- temp %>% filter(!is.na(x), !is.na(y)) #EM edit: remove NA
  regmod <- "y ~ a * exp(-b * x)"
  ones <- c(a=1, b=1) # all ones start
  test.start <- c(a=100, b=0.01)
  anmrtx <- try(nlxb(regmod, start=test.start, trace=FALSE, data=temp))
  S1 <- as.numeric(anmrtx$coef[2])
  
  # S3 = nonlinear fit of an exponential function for S over n350 - n400
  y <- as.numeric(unlist(S3.alpha)) #EM added "unlist"
  X <- seq(350,400,2.5)
  temp <- data.frame(y=y,x=X)
  temp <- temp %>% filter(!is.na(x), !is.na(y))  #EM edit: remove NA
  regmod <- "y ~ a * exp(-b * x)"
  ones <- c(a=1, b=1) # all ones start
  test.start <- c(a=100, b=0.01)
  anmrtx <- try(nlxb(regmod, start=test.start, trace=FALSE, data=temp))
  S3 <- as.numeric(anmrtx$coef[2])
  SR <- S1/S3
  return(SR)
}

# Slope Ratio (SR) [runs very slowly as apply(), would be nice to functionalize in purrr, but tricky without the by_row function which has been elimitated from purrr]
data$SR <- apply(data, 1, calculate.SR)

# 2. SUVA254 
# SUVAS is already derived in .par file as SAC254 (appears correct)

# 3. E2:E3
## [see Spencer et al 2009, doi:10.1029/2008GL036831]
## this is also called E2:E3 - see Helms et al 2008, Limnology & Oceanography 53(3): 955-969
data$E2E3 <- data$`250.00`/data$`365.00` #aka a250:a365
#Spencer 2012, doi:10.1029/2011JG001928 talks about using Napierian, but it works out mathematically to be the same with alpha (Abs/m) or a [as alpha times log(10)] 

# 4. E4:E6
# indicator of humification, E4:E6; alternatively SUVA is used for this - see Helms 2008 pg 955
data$E4E6 <- data$`465.00`/data$`665.00`

# 5. total CDOM absorption calculated as the integrated absorption from 250 to 450 nm [see Helms p959]
CDOM.fp <- data[,c(39:103)] # names(data)[c(39,103)] to confirm columns are the right wavelengths
data$CDOM.total <- rowSums(CDOM.fp, na.rm = TRUE)*200 # the 200 is for length of the integrated spectrum in nm

# 6. output the indices
indices <- data[,c(224,1,2,225:228)]
write.csv(indices,paste0(data_path,"/indices.csv"))
```

```{r}
indices_trim <- indices %>%
  distinct() %>%
  arrange(spectroTime)
```

Check SR plot:
```{r}
indices_trim %>%
  filter(SR < 10, SR > -10) %>%
  ggplot(aes(spectroTime,SR)) +
  geom_point()
```


Try to merge in data from excel sheet
```{r}
library(readxl)
xl <- read_excel("/Users/markjohnson/Documents/research/R scripts/MT agricultural modeling/data/Rodolfo_spectro_2014/Spectrolyzer_290216.xlsx")
xl$Day <- day(xl$Day) 
# only keep 2014 data
xl <- subset(xl, Year == 2014)
codes <- read_excel("/Users/markjohnson/Documents/research/R scripts/MT agricultural modeling/data/Rodolfo_spectro_2014/sample_codes.xlsx")

indices.codes <- merge(indices,codes)
indices.codes.classes <- merge(indices.codes,xl, by.x = "Code", by.y = "Samples original labels")

write.csv(indices.codes,paste0(data_path,"/indices.codes.csv"))
write.csv(indices.codes.classes,paste0(data_path,"/indices.codes.classes.csv"))


```

