--- 
title: "Quantifying synchrony and variability in source water quality across a relatively undisturbed nested catchment: contibutions to characterizing a protected water supply area to better understand how forest management strategies influence drinking water treatability and outcomes"
author: "Hannah J. McSorley"
date: "April 2020"
site: bookdown::bookdown_site
output:
  bookdown::pdf_book
documentclass: ubcthesis
classoption: oneside
bibliography: thesis.bib
biblio-style: apalike
link-citations: yes
description: "Master's thesis"
---

# List of Abbreviations

```{r abbreviations, eval=T, echo=F}
abbreviations <- read.table('acronyms.csv', sep=',', comment='')

knitr::kable(abbreviations,
  booktabs = TRUE, escape=FALSE,
  longtable=TRUE,
  col.names = c('Short','Long')
  )
```

# Acknowledgements

This research work would not have been possible without the support and accommodation of the Capital Regional District (CRD) Watershed Protection and Management Division, Integrated Water Services (IWS) (Victoria, BC). In particular, we would like to acknowledge the help, support and assistance provided by the following people, as well as the entire Field Operations Staff  

* Tobi Gardner  | Senior Hydrologist
* Joel Ussery | Manager, Resource Planning
* Annette Constabel | Senior Manager
* Christoph Moch  | Manager, Water Quality Operations
* Kathy Haesevoats  | Watershed Technologist
* Ryan Biggs  | Watershed Technician 2, Resource Planning(?)
* Burn Hemus  | ?
* Jessica Dupuis  | ?? Water Quality Operations 
* Nigel Burrows | Manager Watershed Fire, Security and Emergency Response
* Patrick McCoubrey | Security Chargehand
* Devon Barnes | Watershed Protection Senior Supervisor  


  
This research also would not have been possible without the support and encouragement from academic supervisors and partners from the NSERC forWater Network for Forested Drinking Water Source Protection Technologies:  

* Bill Floyd  | Academic co-supervisor | Adjunct Professor, Geography, Vancouver Island University & Research Hydrologist, BC-FLNRO
* Mark Johnson  | Academic co-supervisor | Professor and Canada Research Chair, University of British Columbia
* Mike Stone  | Professor, Faculty of Environment, Dept. of Geography and Environmental Management, University of Waterloo
* Dana Harriman | Network Manager, University of Waterloo
* Monica Emelko | Principle Investigator, Scientific Director, University of Waterloo
* Uldis Silins  | Co-Principle Investigator, Co-Scientific Director, University of Alberta
* Danielle Lindamood |(former) Knowledge Mobilization Manager
* Allie Dusome | Communications Officer, the Water Institute, University of Waterloo
* Axel Anderson	| Professor, Faculty of Agricultural, Life and Environmental Science, Renewable Resources Dept., University of Alberta  

  
For help with field installations and streamflow gauging, a big thanks to my former field partner, Stewart Butler, of Bill Floyd's Coastal Hydrology Research Lab; thanks Stew. Thanks also to Alison Bishop for field assistance during the winter of 2019/2020.    

For the love of data science, I am grateful for Jenny Byran's online resources, StackOverflow (http://stackoverflow.com) for the solution to so many coding challenges. Thank you to RStudio for making a functional and friendly IDE for the R programming language and to GitHub for making version control streamlined and reproducibls. Cheers to Hadley Wickham for the tidyverse, Yihui Xie for the bookdown package (in which I wrote this thesis), and Jake Lever (https://github.com/jakelever) for making the R bookdown skeleton code for a UBC thesis available on GitHub.

Last but certainly not least, thanks to my friends and family for encouraging and supporting me in my scientific and academic pursuits. I really appreciate all the love. 

# Dedication

To Stack Overflow, forWater, Tigh Club Athletics, Kananaskis Hydrology friends, everyone who has ever nerded out on water science and each person who reads this thesis in it's entirety. 

\mainmatter

<!--chapter:end:index.Rmd-->

# Introduction

Here is the introduction to this thesis. I will do several things. It is heavily based on previous seminal work on penguins [@meyer2003pressures].


<!--chapter:end:01-intro.Rmd-->

# First Chapter of Research

Here is a research chapter. Look a graph in Figure \@ref(fig:myfigure).

```{r libraries, include=FALSE}
library(knitr)
library(dplyr)
library(lattice)

knitr::opts_chunk$set(echo = TRUE)
```

```{r myfigure, echo=F, eval=T, fig.width=9, fig.asp=1.0,  fig.cap='(ref:myfigure)'}
data <- data.frame(x=runif(10),y=runif(10))
xyplot(y~x, data, cex=2)
```

(ref:myfigure) Here is a figure caption.

Also check out the associated data in Table \@ref(tab:mytable).

```{r mytable, echo=F, eval=T}
knitr::kable(data, 
             booktabs = TRUE, escape=FALSE,
             caption = 'The randomly generated data used for this research.'
             )
```


<!--chapter:end:02-research.Rmd-->

---
output:
  word_document: default
  html_document: default
---
# Conclusions

I did several things and will now discuss why they are good.

<!--chapter:end:03-conclusions.Rmd-->

